### 2015-02-27 paper/figure3.tex
Initial commit

% !TEX root = paper.tex
% !TEX encoding = UTF-8 Unicode

\begin{figure*}[t]
\begin{subfigure}[b]{.5\linewidth}
\begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
\begin{axis}[
    ybar,
    enlargelimits=0.15,
    legend style={at={(0.5,1.05)},anchor=south},
   ylabel={Mean Adequacy Score by Participant},
   xlabel={Post-Editor},
   % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
    xtick={0,1,2,3,4,5,6},
    xticklabels={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
	xtick pos=left,
	ytick pos=left,
	ylabel shift={-0.15cm},
    %xtick=data,
    %nodes near coords,
    %nodes near coords align={vertical},
    bar width=5pt
    ]

\addplot coordinates { (0,7.0) (0,6.1)};
\addplot coordinates { (1,8.0) (2,9.8) (3,9.0) (4,8.2) (5,7.4) (6,7.7)};
\addplot coordinates { (1,7.6) (2,9.3) (3,8.8) (4,7.6) (5,6.7) (6,7.1)};

\addplot[red,sharp plot,update limits=false] 
	coordinates {(-1,6.1) (8,6.1)};
	%node[above] at (axis cs:3,6.1) {Unedited MT};

%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
\legend{Monolingual PE with Alignments, PE with Alignments,PE no Alignments}
\end{axis}
\end{tikzpicture}
\caption{Russian-English}
\label{fig:mean_adequacy_score_per_posteditor_ru}
\end{subfigure}
\begin{subfigure}[b]{.5\linewidth}
\begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
\begin{axis}[
    ybar,
    enlargelimits=0.15,
    legend style={at={(0.5,1.05)},anchor=south},
%   ylabel={Mean Adequacy Score by Participant},
   xlabel={Post-Editor},
   % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
    xtick={1,2,3,4},
    xticklabels={PE7,PE8,PE9,PE10},
	xtick pos=left,
	ytick pos=left,
	ylabel shift={-0.15cm},
	ymin=6,
	ymax=10,
    %xtick=data,
    %nodes near coords,
    %nodes near coords align={vertical},
    bar width=5pt
    ]

\addplot coordinates {};
\addplot coordinates {(1,8.8) (2,8.461538461538462) (3,8.56) (4,8.76923076923077) };
\addplot coordinates {(1,8.23076923076923) (2,8.72) (3,8.461538461538462) (4,8.88) };
\addplot[red,sharp plot,update limits=false] coordinates { (-1,7.686274509803922) (12,7.686274509803922) };

%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
\legend{PE with Alignments,PE no Alignments}
\end{axis}
\end{tikzpicture}
\caption{Spanish-English}
\label{fig:mean_adequacy_score_per_posteditor_es}
\end{subfigure}
\caption{Mean adequacy score per post-editor. The red horizontal line indicates the mean adequacy score (Russian-English: 6.1; Spanish-English: 7.7) of the unedited MT.}
\label{fig:mean_adequacy_score_per_posteditor}
\end{figure*}

### 2015-02-27 paper/paper_abstract.tex
Initial commit

% !TEX root = paper.tex
% !TEX encoding = UTF-8 Unicode

\begin{abstract}
%
Phrase-based machine translation can be configured to produce alignment data that indicates which machine translated target language words correspond to which original source language words.
%
In most prior work that examined the efficacy of post-editing machine translation, post-editors were presented with machine translations (and in most cases the original source language sentences) without also being presented with source-to-target alignment links.
%
We select two news articles, and ask six Russian-English bilinguals to post-edit English machine translation results, in some cases using alignments and in other cases without.
%
We obtain human adequacy judgements of the post-edited sentences, 
%
%and demonstrate
%along with human adequacy judgements for the unedited machine translations and the monolingual post-edited translations of \citet{2014_WMT_Schwartz_etal}.
%
%In this work, we 
and demonstrate that post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
%
%We also find that monolingual post-edited translations are 
%
%In this work, we confirm prior work indicating that bilingual 
%
%As part of the Workshop on Statistical Machine Translation, \citet{2014_WMT_Schwartz_etal} examined the extent to which monolingual native English speakers were able to post-edit machine translation of news articles into fluent, adequate English translations of Russian source sentences.
%
\end{abstract}

### 2015-02-27 paper/paper_conclusion.tex
Initial commit

% !TEX root = paper.tex
% !TEX encoding = UTF-8 Unicode

\section{Conclusion}

Our results indicate that, at least for this language pair and this data set, post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
%
%Our results indicate that this finding holds across participants and across segments of varying MT quality. 
%
This result holds across participants, and is strongest when MT quality is poor.

### 2015-02-27 paper/paper_intro.tex
Initial commit

% !TEX root = paper.tex
% !TEX encoding = UTF-8 Unicode

\section{Introduction}

Post-editing is the process whereby a human user corrects the output of a machine translation system.
%
The use of basic post-editing tools by bilingual human translators has been shown to yield substantial increases in terms of productivity \citep{2010_PBML_Plitt_Masselot} as well as improvements in translation quality \citep{2013_CHI_Green_etal} when compared to bilingual human translators working without assistance from machine translation and post-editing tools.
%
More sophisticated interactive interfaces \citep{2000_NAACL_Langlais_etal,2009_CL_Barrachina,2009_ACL_Koehn,2012_AMTA_Denkowski_Lavie} may also provide benefit \citep{2009_MT_Koehn}.

Small-scale studies have suggested that monolingual human post-editors, working without knowledge of the source language, can also improve the quality of machine translation output \citep{2005_NIST_CallisonBurch,2010_NAACL_Koehn,2013_WPTP_Mitchell_etal}, especially if well-designed tools provide automated linguistic analysis of source sentences \citep{2009_EACL_Albrecht_etal}.
%
\citet{2014_WMT_Schwartz_etal} confirmed this result with eight monolingual post-editors on a larger 3000 sentence test corpus.
%
\citet{2014_WPTP_Schwartz} demonstrated that a monolingual post-editor who is a domain expert in the translated material can successfully post-edit.

In this work, we conduct a bilingual post-editing experiment (\S\ref{sec:methodology}), in which six Russian-English bilingual translation students were asked to post-edit news articles that were previously machine translated from Russian into English.
%
We find (\S\ref{sec:results}) that post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.

### 2015-02-27 paper/paper_methodology.tex
Initial commit

% !TEX root = paper.tex
% !TEX encoding = UTF-8 Unicode

\section{Methodology}
\label{sec:methodology}

\begin{table*}[t]
\begin{subtable}[b]{.5\linewidth}
\begin{center}
\begin{tabular} { | c | p{66mm} | }
\hline
  12 & The post-edited translation is superior to the reference translation \\ \hline
  10 & The meaning of the Russian sentence is fully conveyed in the English translation \\ \hline
  8 & Most of the meaning of the Russian sentence is conveyed in the English translation \\ \hline
  6 & The English translation misunderstands the Russian sentence in a major way, or has many small mistakes \\ \hline
  4 & Very little information from the Russian sentence is conveyed in the English translation \\ \hline
  2 & The English translation makes no sense at all \\ \hline
\end{tabular}
\end{center}
\caption{Russian-English}
\end{subtable}
\begin{subtable}[b]{.5\linewidth}
\begin{center}
\begin{tabular} { | c | p{66mm} | }
\hline
  10 & The meaning of the Spanish sentence is fully conveyed in the English translation \\ \hline
%  9 & The English translation contains one minor error \\ \hline
  8 & Most of the meaning of the Spanish sentence is conveyed in the English translation \\ \hline
  6 & The English translation misunderstands the Spanish sentence in a major way, or has many small mistakes \\ \hline
  4 & Very little information from the Spanish sentence is conveyed in the English translation \\ \hline
  2 & The English translation makes no sense at all \\ \hline
\end{tabular}
\end{center}
\caption{Spanish-English}
\label{judge_guidelines_spanish}
\end{subtable}
\caption{Adequacy evaluation guidelines for bilingual Russian-English human judges \citep{2014_WMT_Schwartz_etal}, and for bilingual Spanish-English human judges. Because no reference translation was available for Spanish-English, the 12 category is omitted.}
\label{judge_guidelines}
\end{table*}

\subsection{Participants}

There were six participants who served as post-editors in this study, all of whom were paid for their time.
%
These participants were all English-Russian bilinguals.
%
Four of the six bilingual participants (PE2, PE3, PE4, \& PE6) had Russian as their first language (L1) and were highly proficient in English as their second language (L2).
%
The other two bilingual participants (PE1 \& PE5) had English as their first language and were highly proficient in Russian as their second language.
%
Three of the six bilingual participants were graduate students and three were undergraduate students; all were enrolled in a Russian Translation program at an American university. %and three were undergraduate students in the same program.
%a Russian Translation program at the same American university.

%In addition, we made use of monolingual post-editing data previously released by \citet{2014_WMT_Schwartz_etal}.
%
%The relevant participant in that study was a native English speaker with no knowledge of Russian.

\todo[inline]{Add Spanish paragraph here}

\subsection{Materials}

We selected as source texts a subset of the texts from the 2014 Workshop on Statistical Machine Translation (WMT-14) shared translation task \citep{2014_WMT_Bojar_etal}.
%
Source texts were news articles covering world news events in late 2013.
%
The first text (Doc A) was originally a Russian-language BBC news article covering Syrian chemical weapons.
%
The second text (Doc B) was originally an English-language news article covering U.S. spying policy.
%
The texts were divided into segments that corresponded to sentences or stand-alone phrases (typically corresponding to news headlines, captions, or cutlines).
%
Segments in Doc A varied in length from 3 to 35 words (mean length 17 words); 
%
segments in Doc B varied in length from 9 to 55 words (mean length 23 words).

Professional translations of Doc A into English and Doc B into Russian were commissioned as part of the WMT-14 shared translation task \citep{2014_WMT_Bojar_etal}.
%
%Doc A consists of 27 segments; Doc B has 28 segments.
%
The Russian version of each text was translated automatically using Moses \citep{2007_ACL_Koehn} by \citet{2014_WMT_Schwartz_etal} as part of their WMT14 shared task submission.
%
As a side effect of the phrase-based MT process, Moses can be configured to produce alignment links, indicating which target language words were produced from which source language words.
%
To enable maximal comparability with the post-editing results of \citet{2014_WMT_Schwartz_etal}, we make use of those machine translations and alignments in this work.

\todo[inline]{Add Spanish paragraph here}

Each text was presented to post-editors in one of two variant modalities using the post-editing interface of \citet{2014_WMT_Schwartz_etal}. 
%
In both variants, each Russian source segment was presented along with the corresponding machine translated English segment; a text field (initially populated with the machine translated segment) where the post-editor could make changes was also presented.
%
In variant 1, the alignment links produced by Moses were graphically displayed, linking source words to their corresponding machine translated target words.
%
In variant 2, the alignment links were omitted from the visualization interface.

\input{figure1}

Each participant was instructed to edit one of the two texts using the interface where alignment links were shown,
%
and to edit the other text using the interface where alignment links were omitted.
%
Participants post-edited the two texts in one session lasting less than two hours, although there were no time limits set for the task.
%
Post-Editors 2, 4, and 6 were assigned to post-edit Doc A using the variant 1 interface that displayed alignments, and Doc B using the variant 2 interface that omitted alignments.
%
Post-Editors 1, 3, and 5 were assigned Doc A using variant 2 and Doc B using the variant 1 interface.

%For each of the segments there was also a reference translation created by XXXX.

\todo[inline]{Add Spanish paragraph here}

\subsection{Procedure}

Participants performed the test individually in an office setting and were instructed to minimally post-edit. 
%
Specifically, they were asked to disregard issues of style and to focus on 
%
a) how well the translation conveyed the meaning of the source text, and 
%
b) the grammatical correctness of the translated segments. 
%
Participants sat in front of a computer that displayed the source texts divided up into segments \cite[Figure 1]{2014_WMT_Schwartz_etal}. % (see \citet{2014_WMT_Schwartz_etal}).
%
Directly below each source text segment, its machine translation was displayed.
%
Below that was an active response area, where participants were asked to carry out the post-editing.
%
The only data collected was the final post-edited output and the overall time taken per text.

\todo[inline]{Add Spanish paragraph here}

### 2015-02-27 paper/paper_results.tex
Initial commit

% !TEX root = paper.tex
% !TEX encoding = UTF-8 Unicode

\input{figure2}

\section{Results}
\label{sec:results}

%\subsection{Rating of translations}

An experienced English-Russian translator and grader rated all post-edited segments as well as the MT segments.%
%
\footnote{We include these adequacy judgements, along with the other data and code produced or used in this work, in the attached dataset and software supplements.}
%in both human-readable tabular form and machine-readable CSV form in the attached dataset supplement.}
%
The rater was presented with blocks of 10 lines arranged in a vertical list:
%
the first line was a source segment, 
%
the second was its reference translation, and 
%
below these were eight translations for the segment 
%
(the MT, one monolingual post-edited translation from \citet{2014_WMT_Schwartz_etal}, and six bilingual post-edited translations) 
%
listed in random order. 
%
The rater was asked to classify all the segment translations on an adequacy scale (see Table \Vref{judge_guidelines}) ranging from 2 (translation makes no sense) to 12 (translation is superior to the reference translation).

\todo[inline]{Add Spanish paragraph here}

%The post-edited English segments

The mean adequacy score when bilingual participants were presented with alignments was 8.35.
%
When alignments were omitted from the post-editing tool, the mean adequacy score was 7.85.  
%
A Wilcoxon signed-rank test \citep{1945_Wilcoxon} showed that when participants were presented with alignments the ratings of their translations were significantly higher than when participants post-edited without access to alignments (N = 6, Z = -2.207, p = 0.027).

\todo[inline]{Add Spanish paragraph here}

This finding indicates that, at least for this language pair and data set, bilingual post-editors produce higher quality translations when presented with bilingual alignment links between source words and machine-translated target words.

In addition to rating each post-edited translation, our bilingual human judge rated the adequacy of the unedited MT segments.
%
We thereby obtained direct human judgements of MT quality.%
%
\footnote{Because we care about the adequacy of post-edited translations, we consider actual human judgements to be preferable to automated metrics such as BLEU \citep{2002_ACL_Papineni_etal}, which at best serve as a flawed proxy for human judgements.}
%
We partition the data according to the MT quality as measured by our human judge in terms of adequacy.
%
For each partition, we then calculate the mean adequacy score of post-edited segments, once for the case where post-editors were presented with alignment data, and once for the case where alignments were not presented.
%
In addition, we perform the same average calculation for the monolingual post-edited segments of Docs A and B from \citet{2014_WMT_Schwartz_etal}.
%
The results are shown in Figure \Vref{fig:mean_adequacy_score}.

%\clearpage

\input{figure3}

\input{figure4}

We observe that when MT quality was poor (adequacy categories 2--6), bilingual post-editors consistently produced higher quality post-edited translations when alignments were shown.
%
When MT quality was high (adequacy categories 8--10), little or no impact to adequacy quality was observed when alignments were shown. 
%
By subtracting the adequacy score of each machine translated segment, we obtain the adequacy gain obtained by post-editing.
%
The above effect can be seen clearly in Figure \Vref{fig:mean_adequacy_gain}, where we show mean gain in adequacy over unedited MT;
%
post-editing makes the most difference when MT quality is poor, and in those cases the presence of alignment links improves post-editing as measured by adequacy.

In Figure \ref{fig:mean_adequacy_score_per_posteditor}, we examine the effect that alignment link visualization has on each bilingual post-editor.
%
We observe that post-editing quality varies widely between post-editors (with PE2 and PE3 performing best).
%
For all six bilingual post-editors, we observe higher mean adequacy scores when alignment links were presented than when they were omitted from the post-editing tool.
%
We also note that when alignment links were absent, one bilingual post-editor (PE5) performed worse than the monolingual post-editor (PE0) from \citet{2014_WMT_Schwartz_etal}.
%
When compared to the unedited machine translations, post-editing resulted in improved mean adequacy for all post-editors, both bilingual and monolingual.

Finally, in Figure \ref{fig:percentage_segments} we present histograms graphing the percentage of segments in each adequacy category.
%
We observe that the majority of unedited machine translations are of relatively poor quality, falling mostly into categories 4 and 6. %, and a few scoring as 12.
%
%The monolingual post-editor from \citet{2014_WMT_Schwartz_etal} was able to skew the quality histogram somewhat to the right, with most segments scored as 6 or 10, and a few scored as better than the reference (12).
The monolingual post-editor improved MT quality somewhat, with most segments scoring as 6 or 10.
%
The histogram for bilingual post-editors using no alignments skewed further to the right, peaking at 8.
%
The histogram for bilingual post-editors with access to alignments skews farthest to the right, peaking at 10.

### 2015-02-27 paper/paper_title.tex
Initial commit

% !TEX root = paper.tex
% !TEX encoding = UTF-8 Unicode

\title{The Effect of Word Alignments in Bilingual and Monolingual Post-Editing}

\author{%
        {}\\
	    {}\\
	    {}\\
	    {}\\
	    {\tt}
}

\date{}

### 2015-02-27 old_scripts/calculate_per_category_percentages.rb

@@ -1,0 +1,25 @@
+#!/usr/bin/ruby
+
+possible_values=[2,4,6,8,10,12]
+counts=Hash.new{|k,v| k[v]=0.0}
+data_points=0
+
+STDIN.each_line{ |line|
+
+	if line=~/[[:alpha:]]/
+		puts line
+	else
+		value=line.strip.to_i
+		counts[value] += 1
+		data_points   += 1
+		
+	end
+}
+
+possible_values.each{ |value|
+
+	decimal_value = counts[value]/data_points
+	percentage = (decimal_value*100).round(0)
+	puts "#{percentage}\\%"
+
+}

### 2015-02-27 old_scripts/extract-individual-results.sh

@@ -1,0 +1,20 @@
+#!/bin/bash
+
+codes="mt s1 s2 s3 s4"
+docs="es-en.1 es-en.2"
+
+for code in ${codes}; do
+	analysis/scored.tsv
+	grep "\t${code}$" analysis/scored.tsv > "analysis_per_user/scored.${user}.tsv"
+
+	for doc in ${docs}; do
+		echo "${user}" > ${doc}.${user}.scores
+		grep "\t${code}$" final-results.csv | grep "^${doc}" | cut -f 3 >> ${doc}.${user}.scores
+	done
+
+done
+
+
+for doc in ${docs}; do
+	paste ${doc}.moses.scores ${doc}.s*-en.scores > ${doc}.scores.csv
+done

### 2015-02-27 scripts/data_to_tsv.rb

@@ -1,0 +1,73 @@
+#!/usr/bin/ruby
+
+doc_names=[
+	"es-en.1",
+	"es-en.2"
+]
+
+comment="----"
+mt_files={
+	"es-en.1"=>"mt/mt.es-en.1",
+	"es-en.2"=>"mt/mt.es-en.2",
+}
+
+def print(document, line, score, segment, subject)
+	puts "#{document}\t#{line}\t#{score}\t#{segment}\t#{subject}"
+end
+
+
+
+results_files={
+
+	"es-en.1"=>
+	{
+		"s1"=>"results/subject1/mt.es-en.1.2015-01-23_09-02-38-S1.output.txt",  
+		"s2"=>"results/subject2/mt.es-en.1.Subject2.2015-01-23_12-21-01.output.txt",
+		"s3"=>"results/subject3/mt.es-en.1.Subject3.2015-01-23_14-20-59.output.txt",
+		"s4"=>"results/subject4/mt.es-en.1.subject_4.2015-01-24_09-52-43.output.txt"
+	},
+	
+	"es-en.2"=>
+	{
+		"s1"=>"results/subject1/mt.es-en.2.2015-01-23_09-22-13-S1.output.txt",
+		"s2"=>"results/subject2/mt.es-en.2.subject2.2015-01-23_12-00-39.output.txt",
+		"s3"=>"results/subject3/mt.es-en.2.Subject3.2015-01-23_14-37-22.output.txt",
+		"s4"=>"results/subject4/mt.es-en.2.Subject_4.2015-01-24_09-39-30.output.txt"
+	}
+
+}
+
+doc_names=results_files.keys.sort
+
+results_files.each_pair{ |doc_name,results_file|
+
+	subjects=results_file.keys.sort
+
+	results=Hash.new
+	results_file.each_pair{|subject,filename|
+		results[subject]=File.readlines(filename)
+	}
+
+	mt=Array.new
+	source=Array.new
+
+	File.open(mt_files[doc_name]).each_line {|line|
+		source_line, character_alignment, word_alignment, mt_line = line.strip.split("\t")
+		source.push(source_line.strip)
+		mt.push(mt_line.strip)
+	}
+
+	0.upto(source.size-1) {|line_number|
+		print("", "", comment, "", "")
+		print("", "", comment, "", "")
+		print("", "", comment, "", "")
+		print(doc_name, line_number, comment, source[line_number], "")
[…]

### 2015-02-27 scripts/focus.sh

@@ -1,0 +1,12 @@
+#!/bin/bash
+
+for s in 1 2 3 4; do
+
+	for doc in es-en.1 es-en.2; do
+
+		#echo "./scripts/focus.rb ${doc} s${s} < results/subject${s}/mt.${doc}*.log.txt"
+		./scripts/focus.rb ${doc} s${s} < results/subject${s}/mt.${doc}*.log.txt
+
+	done
+
+done

### 2015-02-27 scripts/per_user.rb

@@ -1,0 +1,61 @@
+#!/usr/bin/ruby
+
+def print(doc,sentence_number,who,score)
+	align=alignments_were_present(doc,who)
+	puts "#{doc}\t#{sentence_number}\t#{who}\t#{score}\t#{align}"
+end
+
+
+def alignments_were_present(doc,who)
+
+	if (who=="mt")
+		return ""
+	end
+
+	if (doc=="es-en.1")
+		if (who=="s1" || who=="s3")
+			return false
+		elsif (who=="s2" || who=="s4")
+			return true
+		else
+			raise "ERROR:\t#{doc}\t\#{who}"
+		end
+	elsif (doc=="es-en.2")
+		if (who=="s1" || who=="s3")
+			return true
+		elsif (who=="s2" || who=="s4")
+			return false
+		else
+			raise "ERROR:\t#{doc}\t\#{who}"
+		end	
+	else
+		raise "ERROR:\t#{doc}\t\#{who}"
+	end
+
+end
+
+
+bins=Hash.new{|k,v| k[v]=Array.new}
+
+
+STDIN.each_line{|line|
+
+	doc, sentence_number, unused, sentence, score, who = line.gsub('\n','').split("\t")
+	who=who.strip
+	if (who.strip != "")
+		#puts "who='#{who}'\t#{line}"
+		score=score.strip.to_i
+		
+#		if (score==12)
+#			new_score=10
+#		elsif (score==10)
+#			new_score=9
+#		else
+#			new_score=score
+#		end
+		
+		print(doc.to_s.strip,sentence_number.to_s.strip,who.to_s.strip,score.to_s.strip)
+	end
+
+
+}

### 2015-02-27 paper/paper_methodology.tex
More work

@@
 \caption{Russian-English}
+\label{judge_guidelines_russian}
 \end{subtable}
@@
 \end{subtable}
-\caption{Adequacy evaluation guidelines for bilingual Russian-English human judges \citep{2014_WMT_Schwartz_etal}, and for bilingual Spanish-English human judges.
+\caption{Adequacy evaluation guidelines for bilingual Russian-English human judges \citep{2014_WMT_Schwartz_etal}, and for bilingual Spanish-English human judges \citep{2009_EACL_Albrecht_etal}.
 Because no reference translation was available for Spanish-English, the 12 category is omitted.}
@@
 
-\subsection{Participants}
-
-There were six participants who served as post-editors in this study, all of whom were paid for their time.
+\subsection{Russian-English Bilingual Participants}
+There were six participants who served as post-editors in the Russian-English portion of this study, all of whom were paid for their time.
 %
@@
 %
-Three of the six bilingual participants were graduate students and three were undergraduate students; all were enrolled in a Russian Translation program at an American university.
+Three of the six bilingual participants were graduate students and three were undergraduate students; all were enrolled in a university Russian Translation program.
 %and three were undergraduate students in the same program.
@@
 
-\todo[inline]{Add Spanish paragraph here}
+\subsubsection{Spanish-English Bilingual Participants}
 
-\subsection{Materials}
+There were four participants (PE7, PE8, PE9, PE10) who served as post-editors in this portion of the study, all of whom were paid for their time. 
+%
+They were all Spanish-English bilinguals with English as their first language (L1) and highly proficient in Spanish as their second language (L2). 
+%
+The four were second year students in a university Master of Spanish Translation program.
+
+\subsection{Russian Data}
 
@@
 
-\todo[inline]{Add Spanish paragraph here}
+\input{alignments_true}
+
+\subsection{Spanish Data}
+
+Two Spanish source texts were selected. Both were extracts from a news article from a Spanish newspaper covering current world news events. 
+%
+The two texts were divided up into segments that corresponded to sentences or stand alone phrases. 
+%
+The first text (Doc C) had 26 segments that varied in length from 4 to 24 words (mean length 15 words) and the second text (Doc D) had 25 segments that varied in length from 4 to 28 words (mean length 16 words).
+%
+No reference translations exist for either Spanish text.
+
+The Spanish source texts were translated automatically using the Microsoft Bing Translator through its online developer API.
+%
+Bing Translator, when accessed via the developer API, can be configured to return character-level alignment links from source characters to target characters, in addition to  translated target language sentences.
+%
+Our scripts derive word alignments from the character alignments returned by the Bing Translator API.
+
+\subsection{Russian-English Post-Editing Interface}
 
@@
 In variant 2, the alignment links were omitted from the visualization interface.
-
-\input{figure1}
 
@@
 
-\todo[inline]{Add Spanish paragraph here}
+\subsection{Spanish-English Post-Editing Interface}
+
+Participants post-edited one text using the interface where alignment links were shown and the other text using the interface where alignment links were omitted. 
+%
+Participants post-edited the two texts in one session lasting less than one hour. 
+%
+Post-editors 7 and 9 edited Doc C using the interface that omitted the alignments and Doc D using the interface that displayed the alignments. 
+%
+Post-editors 8 and 10 edited Doc C using the interface that displayed the alignments and Doc D using the interface that omitted the alignments.
+
+\input{figure1}
 
@@
 %
-Specifically, they were asked to disregard issues of style and to focus on 
+Specifically, participants were asked to disregard issues of style and to focus on 
 %
@@
 %
-Participants sat in front of a computer that displayed the source texts divided up into segments \cite[Figure 1]{2014_WMT_Schwartz_etal}. % (see \citet{2014_WMT_Schwartz_etal}).
+Participants sat in front of a computer that displayed the source texts divided up into segments (see Figure \ref{fig:screenshot_true} \vpageref[above]{fig:screenshot_true}).
+% (see \citet{2014_WMT_Schwartz_etal}).
 %
@@
 Below that was an active response area, where participants were asked to carry out the post-editing.
+
+During initial data collection (the Russian-English condition), the only data collected was the final post-edited output and the overall time taken per text.
 %
-The only data collected was the final post-edited output and the overall time taken per text.
+Subsequently, we enhanced the post-editing software with additional logging functionality, enabling the software to record key-logging and mouse-logging data.
+%
+For the subsequent Spanish-English condition, this enhanced software was utilized; for this condition millisecond-precision keyboard-event and mouse-event logs were recorded in addition to collecting final post-edited output and overall time taken per text.
 
-\todo[inline]{Add Spanish paragraph here}
+We believe that scientific inquiry is at its strongest when experiments can be easily replicated, and when the raw and processed data from such experiments can be directly verified by reviewers, readers, and other experimenters.
+%
+In that spirit, all data and code produced or used in this work are provided in the attached dataset and software supplements.
+%
+This includes all logs, along with raw machine translation output, alignment data, post-edited output, adequacy judgements, post-editing software, and supplementary scripts.

### 2015-02-27 paper/paper_results.tex
More work

@@
 
-\section{Results}
-\label{sec:results}
+\subsection{Rating Adequacy of Russian-English}
 
@@
 An experienced English-Russian translator and grader rated all post-edited segments as well as the MT segments.%
-%
-\footnote{We include these adequacy judgements, along with the other data and code produced or used in this work, in the attached dataset and software supplements.}
 %in both human-readable tabular form and machine-readable CSV form in the attached dataset supplement.}
@@
 %
-The rater was asked to classify all the segment translations on an adequacy scale (see Table \Vref{judge_guidelines}) ranging from 2 (translation makes no sense) to 12 (translation is superior to the reference translation).
+The rater was asked to classify all the segment translations on an adequacy scale (see Table \Vref{judge_guidelines_russian}) ranging from 2 (translation makes no sense) to 12 (translation is superior to the reference translation).
 
-\todo[inline]{Add Spanish paragraph here}
+\subsection{Rating Adequacy of Russian-English}
+
+One experienced Spanish-English translator and grader and one Spanish-English bilingual rated all post-edited segments as well as the MT segments.
+%
+They did this in cooperation.
+%
+The raters were presented with blocks of six lines arranged in a vertical list: the first line was a source segment, the second was its machine translation, and below these were four translations for the segment listed in random order.
+%
+The raters were asked to classify all the segment translations on an adequacy scale (see Table \Vref{judge_guidelines_spanish}) ranging from 2 (translation makes no sense) to 10 (the meaning of the Spanish sentence is fully conveyed in the English translation).
+% 
+For the rating of the segments in this experiment the top category used for the evaluation of the Russian segments was removed because in the Spanish experiment we did not use a reference translation.
+
+\section{Results}
+\label{sec:results}
+
+\subsection{Russian-English Adequacy}
 
@@
 
-\todo[inline]{Add Spanish paragraph here}
+\input{figure3}
+
+\subsection{Spanish-English Adequacy}
+
+The mean adequacy score when Spanish bilingual participants were presented with alignments was 8.65.
+When alignments were omitted from the post-editing tool, the mean adequacy score was 8.57.
+These means were not significantly different.
+
+\subsection{Analysis}
 
@@
 %
-\footnote{Because we care about the adequacy of post-edited translations, we consider actual human judgements to be preferable to automated metrics such as BLEU \citep{2002_ACL_Papineni_etal}, which at best serve as a flawed proxy for human judgements.}
-%
+Because we care about the adequacy of post-edited translations, we consider actual human judgements to be preferable to automated metrics such as BLEU \citep{2002_ACL_Papineni_etal}, which at best serve as a flawed proxy for human judgements.
+
 We partition the data according to the MT quality as measured by our human judge in terms of adequacy.
@@
 %
-The results are shown in Figure \Vref{fig:mean_adequacy_score}.
+The results are shown in Figure \ref{fig:mean_adequacy_score}.
 
 %\clearpage
-
-\input{figure3}
 

### 2015-07-10 paper/figure3.tex
MT Summit, just before adding Isabel's latest

@@
 
-\begin{figure*}[t]
-\begin{subfigure}[b]{.5\linewidth}
+\begin{figure}
+\begin{subfigure}[b]{\linewidth}
+\begin{center}
 \begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
-\begin{axis}[
+\begin{axis}[%scale only axis=true, width=80mm, height=73mm,
     ybar,
@@
 \label{fig:mean_adequacy_score_per_posteditor_ru}
+\end{center}
 \end{subfigure}
-\begin{subfigure}[b]{.5\linewidth}
+\ \\ \ \\
+\begin{subfigure}[b]{\linewidth}
+\begin{center}
 \begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
-\begin{axis}[
+\begin{axis}[%scale only axis=true, width=60mm, height=73mm,
     ybar,
@@
 \end{tikzpicture}
+\end{center}
 \caption{Spanish-English}
@@
 \label{fig:mean_adequacy_score_per_posteditor}
-\end{figure*}
+\end{figure}

### 2015-07-10 paper/paper_abstract.tex
MT Summit, just before adding Isabel's latest

@@
 %
-We select two news articles, and ask six Russian-English bilinguals to post-edit English machine translation results, in some cases using alignments and in other cases without.
+We select four news articles, and ask six Russian-English bilinguals and four Spanish-English bilinguals to post-edit English machine translation results, in some cases using alignments and in other cases without.
 %
@@
 %In this work, we 
-and demonstrate that post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
+and demonstrate that when machine translation quality is low, post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
 %

### 2015-07-10 paper/paper_conclusion.tex
MT Summit, just before adding Isabel's latest

@@
 
-Our results indicate that, at least for this language pair and this data set, post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
+%The question of how a post-editing interface should be configured and presented to users is a fundamentally interdisciplinary and empirical one.
+%
+%Issues of user interface design, human factors, translation studies, and machine translation quality are all likely relevant.
+%
+%Phrase-based machine translation can be configured to produce alignment data that indicates which machine translated target language words correspond to which original source language words.
+%
+%In most prior work that examined the efficacy of post-editing machine translation, post-editors were presented with machine translations (and in most cases the original source language sentences) without also being presented with source-to-target alignment links.
+
+In this work, we observe that when machine translation quality is poor, bilingual post-editors may produce higher quality translations when presented with bilingual alignment links between source words and machine-translated target words.
+%
+%Alternatively, when machine translation quality is high, no effect is seen by presenting alignment visualizations.
+%
+We explain this by hypothesizing that word alignment visualization may enable post-editors to better recover from certain types of translation errors produced by MT systems; when MT quality is high enough that such errors are absent, word alignment visualization may no longer play a restorative role.
+%
+The timing results we observe, while not statistically significant, appear to be consistent with prior work that found per word post-editing times to be shorter for segments that were less cognitively demanding.
+
+%This work begins an attempt to answer two novel questions regarding post-editing interface design: 
+%%
+%To what extent, if at all, does the presentation of source-to-target word-level alignment links affect the quality or speed of post-editing?
+%%
+%Is any such effect, if it exists, dependent on certain aspects of machine translation quality, or on the language pair?
+
+%Our results indicate that, at least for this language pair and this data set, post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
 %
@@
 %
-This result holds across participants, and is strongest when MT quality is poor.
+%This result holds across participants, and is strongest when MT quality is poor.

### 2015-07-10 paper/paper_intro.tex
MT Summit, just before adding Isabel's latest

@@
 
-Small-scale studies have suggested that monolingual human post-editors, working without knowledge of the source language, can also improve the quality of machine translation output \citep{2005_NIST_CallisonBurch,2010_NAACL_Koehn,2013_WPTP_Mitchell_etal}, especially if well-designed tools provide automated linguistic analysis of source sentences \citep{2009_EACL_Albrecht_etal}.
+The question of how a post-editing interface should be configured and presented to users is a fundamentally interdisciplinary and empirical one.
 %
-\citet{2014_WMT_Schwartz_etal} confirmed this result with eight monolingual post-editors on a larger 3000 sentence test corpus.
+Issues of user interface design, human factors, translation studies, and machine translation quality are all likely relevant.
 %
-\citet{2014_WPTP_Schwartz} demonstrated that a monolingual post-editor who is a domain expert in the translated material can successfully post-edit.
+Phrase-based machine translation can be configured to produce alignment data that indicates which machine translated target language words correspond to which original source language words.
+%
+In most prior work that examined the efficacy of post-editing machine translation, post-editors were presented with machine translations (and in most cases the original source language sentences) without also being presented with source-to-target alignment links.
 
-In this work, we conduct a bilingual post-editing experiment (\S\ref{sec:methodology}), in which six Russian-English bilingual translation students were asked to post-edit news articles that were previously machine translated from Russian into English.
+This work begins an attempt to answer two novel questions regarding post-editing interface design: 
 %
-We find (\S\ref{sec:results}) that post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
+To what extent, if at all, does the presentation of source-to-target word-level alignment links affect the quality or speed of post-editing?
+%
+Is any such effect, if it exists, dependent on certain aspects of machine translation quality, or on the language pair?
+
+To address these questions, we conduct a bilingual post-editing experiment (\S\ref{sec:methodology}) where bilingual post-editors are presented with machine translation output of varying quality, with and without word-level alignment link visualization.
+%
+In the first condition, we ask six Russian-English bilingual translation students to post-edit two Russian language news articles starting with relatively low quality English machine translation.
+%
+In the second condition, we ask four Spanish-English bilingual translation students to post-edit two Spanish language news articles starting with relatively high quality English machine translation.
+%
+We find (\S\ref{sec:results}) that when machine translation quality is low, post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
+%
+We find no statistically significant effect when machine translation quality is high.
+%
+We also found that for both Russian-English and Spanish-English the mean post-editing times were shorter for texts with alignment than for texts without alignment.
+These differences were not significant, but the difference for the Russian-English texts approached significance.
+%
+Finally, in \S\ref{sec:background} we briefly survey the current state of post-editing research and situate this work within the context of related work in post-editing.

### 2015-07-10 paper/paper_methodology.tex
MT Summit, just before adding Isabel's latest

@@
 
-\begin{table*}[t]
-\begin{subtable}[b]{.5\linewidth}
-\begin{center}
-\begin{tabular} { | c | p{66mm} | }
-\hline
-  12 & The post-edited translation is superior to the reference translation \\ \hline
-  10 & The meaning of the Russian sentence is fully conveyed in the English translation \\ \hline
-  8 & Most of the meaning of the Russian sentence is conveyed in the English translation \\ \hline
-  6 & The English translation misunderstands the Russian sentence in a major way, or has many small mistakes \\ \hline
-  4 & Very little information from the Russian sentence is conveyed in the English translation \\ \hline
-  2 & The English translation makes no sense at all \\ \hline
-\end{tabular}
-\end{center}
-\caption{Russian-English}
-\label{judge_guidelines_russian}
-\end{subtable}
-\begin{subtable}[b]{.5\linewidth}
-\begin{center}
-\begin{tabular} { | c | p{66mm} | }
-\hline
-  10 & The meaning of the Spanish sentence is fully conveyed in the English translation \\ \hline
-%  9 & The English translation contains one minor error \\ \hline
-  8 & Most of the meaning of the Spanish sentence is conveyed in the English translation \\ \hline
-  6 & The English translation misunderstands the Spanish sentence in a major way, or has many small mistakes \\ \hline
-  4 & Very little information from the Spanish sentence is conveyed in the English translation \\ \hline
-  2 & The English translation makes no sense at all \\ \hline
-\end{tabular}
-\end{center}
-\caption{Spanish-English}
-\label{judge_guidelines_spanish}
-\end{subtable}
-\caption{Adequacy evaluation guidelines for bilingual Russian-English human judges \citep{2014_WMT_Schwartz_etal}, and for bilingual Spanish-English human judges \citep{2009_EACL_Albrecht_etal}.
-Because no reference translation was available for Spanish-English, the 12 category is omitted.}
-\label{judge_guidelines}
-\end{table*}
+We hypothesize that the presentation of word-level alignment links to human post-editors may affect the quality or speed of the resulting output, and that such effects may be dependent on the quality of the underlaying machine translations.
+%
+To test this hypothesis, we conduct a bilingual post-editing experiment  where bilingual post-editors are presented with machine translation output of varying quality, with and without word-level alignment link visualization.
 
-\subsection{Russian-English Bilingual Participants}
+\input{paper_table}
+
+\subsection{Bilingual Participants}
+
+%All participants were bilingual graduate students enrolled in translations studies.
+
+\subsubsection{Russian-English Bilingual Participants}
 There were six participants who served as post-editors in the Russian-English portion of this study, all of whom were paid for their time.
@@
 These participants were all English-Russian bilinguals.
+%
+We designate these participants as PE1--PE6.
 %
@@
 
-There were four participants (PE7, PE8, PE9, PE10) who served as post-editors in this portion of the study, all of whom were paid for their time. 
+There were four participants who served as post-editors in the Spanish-English portion of this study, all of whom were paid for their time. 
 %
-They were all Spanish-English bilinguals with English as their first language (L1) and highly proficient in Spanish as their second language (L2). 
+They were all Spanish-English bilinguals.
 %
-The four were second year students in a university Master of Spanish Translation program.
+We designate these participants as PE7--PE10.
+%
+The first language (L1) of all four participants was English, and all four were highly proficient in Spanish as their second language (L2). 
+%
+These participants were second year students in a university Master of Spanish Translation program.
 
-\subsection{Russian Data}
+\subsection{Source Language Data}
 
-We selected as source texts a subset of the texts from the 2014 Workshop on Statistical Machine Translation (WMT-14) shared translation task \citep{2014_WMT_Bojar_etal}.
+\subsubsection{Russian Data}
+
+For the Russian-English portion of this study, we selected as source texts a subset of the texts from the 2014 Workshop on Statistical Machine Translation (WMT-14) shared translation task \citep{2014_WMT_Bojar_etal}.
 %
@@
 %
-The first text (Doc A) was originally a Russian-language BBC news article covering Syrian chemical weapons.
+The first text was originally a Russian-language BBC news article covering Syrian chemical weapons.
 %
-The second text (Doc B) was originally an English-language news article covering U.S. spying policy.
+The second text was originally an English-language news article covering U.S. spying policy.
 %
-The texts were divided into segments that corresponded to sentences or stand-alone phrases (typically corresponding to news headlines, captions, or cutlines).
+We designate the former as Doc A and the latter as Doc B.
+
+These two texts were each divided into segments (32 and 33 segments, respectively) that corresponded to sentences or stand-alone phrases (typically corresponding to news headlines, captions, or cutlines).
 %
@@
 %
-To enable maximal comparability with the post-editing results of \citet{2014_WMT_Schwartz_etal}, we make use of those machine translations and alignments in this work.
+To enable maximal comparability with the post-editing results of \citet{2014_WMT_Schwartz_etal}, we make use of Russian-English machine translation results and alignments from that work here.
 
-\input{alignments_true}
-
-\subsection{Spanish Data}
+\subsubsection{Spanish Data}
 
@@
 %
-The first text (Doc C) had 26 segments that varied in length from 4 to 24 words (mean length 15 words) and the second text (Doc D) had 25 segments that varied in length from 4 to 28 words (mean length 16 words).
+The first text had 26 segments that varied in length from 4 to 24 words (mean length 15 words) and the second text had 25 segments that varied in length from 4 to 28 words (mean length 16 words).
+%
+We designate the former as Doc C and the latter as Doc D.
 %
@@
 
-The Spanish source texts were translated automatically using the Microsoft Bing Translator through its online developer API.
+The Spanish source texts were translated automatically using Microsoft Bing Translator through its online developer API.
 %
@@
 
-\subsection{Russian-English Post-Editing Interface}
+\subsection{Translation Quality}
+\label{sec:translation_quality}
 
-Each text was presented to post-editors in one of two variant modalities using the post-editing interface of \citet{2014_WMT_Schwartz_etal}. 
+We hypothesize that any effects of word alignment visualization on post-editing may be dependent on the quality of the underlying machine translations displayed to the post-editors.
 %
-In both variants, each Russian source segment was presented along with the corresponding machine translated English segment; a text field (initially populated with the machine translated segment) where the post-editor could make changes was also presented.
+Because we care about the adequacy of post-edited translations, we consider actual human judgements to be preferable to automated metrics such as BLEU \citep{2002_ACL_Papineni_etal}, which at best serve as a flawed proxy for human judgements.
 %
-In variant 1, the alignment links produced by Moses were graphically displayed, linking source words to their corresponding machine translated target words.
+Instead, following \citet{2009_EACL_Albrecht_etal} and \citet{2014_WMT_Schwartz_etal}, we therefore obtained human judgements of translation adequacy for the Russian-English and Spanish-English machine translations used in this study.
+
+The Russian language news articles used in this study have corresponding reference translations.
 %
-In variant 2, the alignment links were omitted from the visualization interface.
+It is therefore possible (although given current machine translation quality, highly unlikely) that machine translation quality for any given segment could conceivably surpass the quality of the corresponding reference translation (if for example, the reference translator makes a mistake).
+%
+For assessing the quality of the Russian-English machine translations, then, we follow the 12-point adequacy scale of \citet{2014_WMT_Schwartz_etal}.
+%
+This adequacy scale is shown in Table \ref{judge_guidelines_russian} \vpageref[above]{judge_guidelines_russian};
+%
+this scale ranges from a low of 2 (the English translation makes no sense at all) to a high of 12 (the translation is superior to the reference).
 
-Each participant was instructed to edit one of the two texts using the interface where alignment links were shown,
+The Spanish language news articles used in this study lack corresponding reference translations.
 %
-and to edit the other text using the interface where alignment links were omitted.
+Thus, unlike the case of our Russian data, no matter how high the quality of machine translations, no Spanish-English machine translation segment could possibly receive a score of 12.
 %
-Participants post-edited the two texts in one session lasting less than two hours, although there were no time limits set for the task.
+For Spanish-English, we therefore follow the 10-point adequacy scale of \citet{2009_EACL_Albrecht_etal}.
 %
-Post-Editors 2, 4, and 6 were assigned to post-edit Doc A using the variant 1 interface that displayed alignments, and Doc B using the variant 2 interface that omitted alignments.
+This adequacy scale is shown in Table \ref{judge_guidelines_spanish} \vpageref[above]{judge_guidelines_spanish};
 %
-Post-Editors 1, 3, and 5 were assigned Doc A using variant 2 and Doc B using the variant 1 interface.
+this scale is very similar to the former, but has a high of 10 (the meaning of the source sentence is fully conveyed in the English translation) instead of 12.
 
-%For each of the segments there was also a reference translation created by XXXX.
+\input{alignments_true}
 
-\subsection{Spanish-English Post-Editing Interface}
+\subsection{Post-Editing Interface}
 
-Participants post-edited one text using the interface where alignment links were shown and the other text using the interface where alignment links were omitted. 
+For this study, we developed a novel post-editing interface, based on the open source software used and released by \citet{2014_WMT_Schwartz_etal}.
 %
-Participants post-edited the two texts in one session lasting less than one hour. 
+Our software is written using Scala \citep{2014_Scala_Odersky}, and is released as open source (see the software supplement that accompanies this work).
 %
-Post-editors 7 and 9 edited Doc C using the interface that omitted the alignments and Doc D using the interface that displayed the alignments. 
+This code constitutes a ground-up rewrite of the Java-based post-editing interface of \citet{2014_WMT_Schwartz_etal}, written using a strict model-view-controller software design pattern to be easy for other researchers to use and extend.
+
+Our post-editing interface can be seen in Figure~\ref{fig:screenshot_true} \vpageref[above]{fig:screenshot_true}.
 %
-Post-editors 8 and 10 edited Doc C using the interface that displayed the alignments and Doc D using the interface that omitted the alignments.
+Each text was presented to post-editors in one of two variant modalities --- word-level alignment links could either be visualized or left absent.
+%
+In both variants, each source language segment was presented along with the corresponding machine translated English segment; a text field (initially populated with the machine translated segment) where the post-editor could make changes was also presented.
+%
+In the first variant, the word-level alignment links produced by the machine translation decoder (Moses for Russian-English, Bing Translator for Spanish-English) were graphically displayed, linking source words to their corresponding machine translated target words.
+%
+In the second variant, the word-level alignment links were omitted from the visualization interface.
 
-\input{figure1}
-
+  \input{figure4}
  \subsection{Procedure}
@@
 This includes all logs, along with raw machine translation output, alignment data, post-edited output, adequacy judgements, post-editing software, and supplementary scripts.
+
+\subsubsection{Russian-English Participant Assignment}
+
+Each participant was instructed to edit one of the two texts using the interface where alignment links were shown,
+%
+and to edit the other text using the interface where alignment links were omitted.
+%
+Participants post-edited the two texts in one session lasting less than two hours, although there were no time limits set for the task.
+%
+Post-Editors 2, 4, and 6 were assigned to post-edit Doc A using the variant 1 interface that displayed alignments, and Doc B using the variant 2 interface that omitted alignments.
+%
+Post-Editors 1, 3, and 5 were assigned Doc A using variant 2 and Doc B using variant 1.
+
+%For each of the segments there was also a reference translation created by XXXX.
+
+\subsubsection{Spanish-English Participant Assignment}
+
+Participants post-edited one text using the interface where alignment links were shown and the other text using the interface where alignment links were omitted. 
+%
+Participants post-edited the two texts in one session lasting less than one hour. 
+%
+Post-editors 7 and 9 edited Doc C using the interface that omitted the alignments and Doc D using the interface that displayed the alignments. 
+%
+Post-editors 8 and 10 edited Doc C using the interface that displayed the alignments and Doc D using the interface that omitted the alignments.

### 2015-07-10 paper/paper_results.tex
MT Summit, just before adding Isabel's latest

--- 2015-02-27 paper/paper_results.tex
@@
 
-\input{figure2}
+\input{figure1}
 
@@
 
+\subsection{Rating Translation Adequacy}
+
+Following the methodology outlined in \S\ref{sec:translation_quality}, all post-edited output as well as all machine translations were evaluated by bilingual human judges using the adequacy scales shown in Table~\ref{judge_guidelines} \vpageref{judge_guidelines}.
+
+\subsubsection{Rating Adequacy of Russian-English}
+
 %\subsection{Rating of translations}
 
-An experienced English-Russian translator and grader rated all post-edited segments as well as the MT segments.%
+Following the adequacy guidelines from \S\ref{sec:translation_quality}, %shown in Table~\ref{judge_guidelines_russian},
 %
-\footnote{We include these adequacy judgements, along with the other data and code produced or used in this work, in the attached dataset and software supplements.}
+an experienced English-Russian translator and grader rated all English output translations of the Russian-English post-edited segments.
+%
+In addition, all English machine translations of the Russian documents were manually rated for adequacy.
+% as well as the machine translation segments.
 %in both human-readable tabular form and machine-readable CSV form in the attached dataset supplement.}
+
+For each segment, the human rater was presented with a vertically-arranged list showing all variants of that segment.
 %
-The rater was presented with blocks of 10 lines arranged in a vertical list:
+The first entry in each list was the segment in the source language (Russian).
 %
-the first line was a source segment, 
+The source segment was followed by the reference translation in English.
 %
-the second was its reference translation, and 
+The subsequent eight entries were English translations of the source segment, presented in a randomized order.
 %
-below these were eight translations for the segment 
+The English translations included the unedited machine translation output, as produced by Moses,
 %
-(the MT, one monolingual post-edited translation from \citet{2014_WMT_Schwartz_etal}, and six bilingual post-edited translations) 
+a post-edited translation produced by a monolingual post-editor from \citet{2014_WMT_Schwartz_etal},
 %
-listed in random order. 
+and the six post-edited translations produced by the Russian-English bilingual post-editors in this study.
+
+All Russian-English translations were rated using the translation adequacy scale in Table \Vref{judge_guidelines_russian}, with possible ratings ranging from  2 (translation makes no sense) to 12 (translation is superior to the reference translation).
+
+%The human rater was presented with blocks of 10 lines arranged in a vertical list:
+%%
+%the first line was a source segment, 
+%%
+%the second was its reference translation, and 
+%%
+%below these were eight translations for the segment 
+%%
+%(the machine translation, one monolingual post-edited translation from \citet{2014_WMT_Schwartz_etal}, and six bilingual post-edited translations) 
+%%
+%listed in random order. 
+%%
+%The rater was asked to classify all the segment translations on an adequacy scale (see Table \Vref{judge_guidelines_russian}) ranging from 2 (translation makes no sense) to 12 (translation is superior to the reference translation).
+
+\subsubsection{Rating Adequacy of Spanish-English}
+
+Following the adequacy guidelines from \S\ref{sec:translation_quality}, 
 %
-The rater was asked to classify all the segment translations on an adequacy scale (see Table \Vref{judge_guidelines}) ranging from 2 (translation makes no sense) to 12 (translation is superior to the reference translation).
+an experienced Spanish-English translator and grader worked in cooperation with a second Spanish-English bilingual to rate all English output translations of the Spanish-English post-edited segments.
+%
+In addition, all English machine translations of the Spanish documents were manually rated for adequacy.
+%
+%One experienced Spanish-English translator and grader and one Spanish-English bilingual rated all post-edited segments as well as the MT segments.
+%%
+%They did this in cooperation.
+For each segment, the human raters were presented with a vertically-arranged list showing all variants of that segment.
+%
+The first entry in each list was the segment in the source language (Spanish).
+%
+The source segment was followed by the reference translation in English.
+%
+The subsequent five entries were English translations of the source segment, presented in a randomized order.
+%
+The English translations included the unedited machine translation output, as produced by Bing Translator,
+%
+and the four post-edited translations produced by the Spanish-English bilingual post-editors in this study.
 
-\todo[inline]{Add Spanish paragraph here}
+Unlike the Russian documents, no reference translation was available for the Spanish documents; for this reason (as described in \S\ref{sec:translation_quality}), the top category (12) used in evaluating Russian-English segments was omitted from the Spanish-English evaluation.
+%
+All Spanish-English translations were rated using the translation adequacy scale in Table \Vref{judge_guidelines_spanish}, with possible ratings ranging from  2 (translation makes no sense) to 10 (the meaning of the Spanish sentence is fully conveyed in the English translation).
+%
+%
+%%
+%The raters were presented with blocks of six lines arranged in a vertical list: the first line was a source segment, the second was its machine translation, and below these were four translations for the segment listed in random order.
+%%
+%The raters were asked to classify all the segment translations on an adequacy scale (see Table \Vref{judge_guidelines_spanish}) ranging from 2 (translation makes no sense) to 10 (the meaning of the Spanish sentence is fully conveyed in the English translation).
+% 
+%For the rating of the segments in this experiment the top category used for the evaluation of the Russian segments was removed because in the Spanish experiment we did not use a reference translation.
+
+\subsection{Adequacy Results}
+
+Figure~\ref{fig:percentage_segments} \vpageref[above]{fig:percentage_segments} presents the percentage of segments judged to be in each adequacy category.
+%
+Mean adequacy scores for each experimental condition are presented in Figure~\ref{fig:mean_adequacy_score} \vpageref[above]{fig:mean_adequacy_score}.
+%
+By subtracting the adequacy score of each machine translated segment, we obtain the adequacy gain obtained by post-editing;
+%
+these values are presented in Figure~\ref{fig:mean_adequacy_gain} \vpageref[above]{fig:mean_adequacy_gain}.
+%The above effect can be seen clearly in Figure \Vref{fig:mean_adequacy_gain}, where we show mean gain in adequacy over unedited MT
+%
+%We also calculate the adequacy improvements of post-edited translations over unedited machine translations; such mean gains in adequacy are presented in Figure~\ref{fig:mean_adequacy_gain} \vpageref[above]{fig:mean_adequacy_gain}.
+%
+Finally, Figure~\ref{fig:mean_adequacy_score_per_posteditor} \vpageref[above]{fig:mean_adequacy_score_per_posteditor} presents mean adequacy score by post-editor.
+%
+We now analyze these results by experimental condition.
+
+\subsubsection{Machine Translation Adequacy}
+
+In Figure~\ref{fig:percentage_segments} \vpageref[above]{fig:percentage_segments}, we observe that the Russian-English machine translation segments tend to be of lower quality (as measured by adequacy), while the Spanish-English machine translation segments tend to be of higher quality.
+%
+Two-thirds of Russian-English machine translation segments are judged to have major errors (ratings 2-6), while one-third are rated as mostly or completely correct (8-12).
+%
+Contrast this with the Spanish-English machine translations segments; 
+%
+less than one-third are judged to have major errors (ratings 2-6), while the majority (over two-thirds) are rated as mostly or completely correct (8-10).
+
+\input{figure2}
+
+\subsubsection{Russian-English Adequacy}
 
@@
 
-\todo[inline]{Add Spanish paragraph here}
+\subsubsection{Spanish-English Adequacy}
 
-This finding indicates that, at least for this language pair and data set, bilingual post-editors produce higher quality translations when presented with bilingual alignment links between source words and machine-translated target words.
+The mean adequacy score when Spanish bilingual participants were presented with alignments was 8.65.
+When alignments were omitted from the post-editing tool, the mean adequacy score was 8.57.
+These means are not significantly different.
 
-In addition to rating each post-edited translation, our bilingual human judge rated the adequacy of the unedited MT segments.
+%Our results suggest that when machine translation quality is low, bilingual post-editors may produce higher quality translations when presented with bilingual alignment links between source words and machine-translated target words.
 %
-We thereby obtained direct human judgements of MT quality.%
-%
-\footnote{Because we care about the adequacy of post-edited translations, we consider actual human judgements to be preferable to automated metrics such as BLEU \citep{2002_ACL_Papineni_etal}, which at best serve as a flawed proxy for human judgements.}
-%
-We partition the data according to the MT quality as measured by our human judge in terms of adequacy.
-%
-For each partition, we then calculate the mean adequacy score of post-edited segments, once for the case where post-editors were presented with alignment data, and once for the case where alignments were not presented.
-%
-In addition, we perform the same average calculation for the monolingual post-edited segments of Docs A and B from \citet{2014_WMT_Schwartz_etal}.
-%
-The results are shown in Figure \Vref{fig:mean_adequacy_score}.
+%In addition to rating each post-edited translation, our bilingual human judge rated the adequacy of the unedited MT segments.
+%%
+%We thereby obtained direct human judgements of MT quality.
+%%
+%Because we care about the adequacy of post-edited translations, we consider actual human judgements to be preferable to automated metrics such as BLEU \citep{2002_ACL_Papineni_etal}, which at best serve as a flawed proxy for human judgements.
+
+%We partition the data according to the MT quality as measured by our human judge in terms of adequacy.
+%%
+%For each partition, we then calculate the mean adequacy score of post-edited segments, once for the case where post-editors were presented with alignment data, and once for the case where alignments were not presented.
+%%
+%In addition, we perform the same average calculation for the monolingual post-edited segments of Docs A and B from \citet{2014_WMT_Schwartz_etal}.
+%%
+%The results are shown in Figure \ref{fig:mean_adequacy_score}.
 
@@
 
-\input{figure4}
+\subsection{Timing Results}
 
-We observe that when MT quality was poor (adequacy categories 2--6), bilingual post-editors consistently produced higher quality post-edited translations when alignments were shown.
+\subsubsection{Russian-English Timing}
+
+The times taken by the Russian-English post-editors to post-edit each text were recorded manually to the nearest minute.
+The mean times were 33 minutes for texts with alignment and 40 minutes for texts without alignment.
+This difference approached significance (p = .082).
+
+\subsubsection{Spanish-English Timing}
+
+The times taken by the Spanish-English post-editors to post-edit each text were recorded by the keylogger to nearest millisecond.
+The mean times were 16.36 minutes for texts with alignment and 16.66 minutes for texts without alignment.
+This difference was not statistically significant.
 %
-When MT quality was high (adequacy categories 8--10), little or no impact to adequacy quality was observed when alignments were shown. 
+The shorter editing times for Spanish-English may in part be explained by the shorter length of these documents.
+
+\section{Analysis and Related Work}
+\label{sec:background}
+
+Our results suggest that when machine translation quality is poor (2--4), bilingual post-editors may produce higher quality translations when presented with bilingual alignment links between source words and machine-translated target words.
 %
-By subtracting the adequacy score of each machine translated segment, we obtain the adequacy gain obtained by post-editing.
+Alternatively, when machine translation quality is high (8--12), no effect is seen by presenting alignment visualizations.
 %
-The above effect can be seen clearly in Figure \Vref{fig:mean_adequacy_gain}, where we show mean gain in adequacy over unedited MT;
+We explain this by hypothesizing that word alignment visualization may enable post-editors to better recover from certain types of translation errors produced by MT systems; when MT quality is high enough that such errors are absent, word alignment visualization may no longer play a restorative role.
+
 %
-post-editing makes the most difference when MT quality is poor, and in those cases the presence of alignment links improves post-editing as measured by adequacy.
+%
+%We observe that when MT quality was poor (adequacy categories 2--6), bilingual post-editors consistently produced higher quality post-edited translations when alignments were shown.
+%
+%On the other hand, when MT quality is high (adequacy categories 8--10), little or no impact to adequacy quality was observed when alignments were shown. 
+%%
+%By subtracting the adequacy score of each machine translated segment, we obtain the adequacy gain obtained by post-editing.
+%%
+%The above effect can be seen clearly in Figure \Vref{fig:mean_adequacy_gain}, where we show mean gain in adequacy over unedited MT;
+%%
+%post-editing makes the most difference when MT quality is poor, and in those cases the presence of alignment links improves post-editing as measured by adequacy.
 
-In Figure \ref{fig:mean_adequacy_score_per_posteditor}, we examine the effect that alignment link visualization has on each bilingual post-editor.
+We examine the effect that alignment link visualization has on each bilingual post-editor in Figure \ref{fig:mean_adequacy_score_per_posteditor} \vpageref[above]{fig:mean_adequacy_score_per_posteditor}.
 %
-We observe that post-editing quality varies widely between post-editors (with PE2 and PE3 performing best).
+In the Russian-English condition, where overall MT quality is poor, we observe that post-editing quality varies widely between post-editors (with PE2 and PE3 performing best).
 %
@@
 %
+On the other hand, in the Spanish-English condition, where overall MT quality is good, we observe relatively little variation in quality between the four post-editors.
+%
 When compared to the unedited machine translations, post-editing resulted in improved mean adequacy for all post-editors, both bilingual and monolingual.
 
-Finally, in Figure \ref{fig:percentage_segments} we present histograms graphing the percentage of segments in each adequacy category.
+Our results also suggest that post-editing time tends to be reduced for texts with alignment. 
 %
-We observe that the majority of unedited machine translations are of relatively poor quality, falling mostly into categories 4 and 6. %, and a few scoring as 12.
+These numerical reductions were consistent across all the Russian-English participants with the exception of PE3, but they were not consistent for the Spanish-English participants.
+
+We hypothesize that texts with alignment are less cognitively demanding to process, and so less effortful to post-edit than texts without alignment. 
 %
-%The monolingual post-editor from \citet{2014_WMT_Schwartz_etal} was able to skew the quality histogram somewhat to the right, with most segments scored as 6 or 10, and a few scored as better than the reference (12).
-The monolingual post-editor improved MT quality somewhat, with most segments scoring as 6 or 10.
+If this is the case, shorter post-editing times for texts with alignment are consistent with previous findings by \citet{2012_AMTA_Koponen_etal}, who found that per word post-editing times were shorter for segments that were less cognitively demanding because of the linguistic structure.
 %
-The histogram for bilingual post-editors using no alignments skewed further to the right, peaking at 8.
-%
-The histogram for bilingual post-editors with access to alignments skews farthest to the right, peaking at 10.
+Related work on cognitive effort in post-editing \citep{2014_AMTA_Lacruz_etal,2014_Lacruz_Shreve} has also shown decreased densities of short pauses when less cognitively demanding segments are post-edited.
+
+%Finally, in Figure \ref{fig:percentage_segments} we present histograms graphing the percentage of segments in each adequacy category.
+%%
+%We observe that the majority of unedited machine translations are of relatively poor quality, falling mostly into categories 4 and 6. %, and a few scoring as 12.
+%%
+%%The monolingual post-editor from \citet{2014_WMT_Schwartz_etal} was able to skew the quality histogram somewhat to the right, with most segments scored as 6 or 10, and a few scored as better than the reference (12).
+%The monolingual post-editor improved MT quality somewhat, with most segments scoring as 6 or 10.
+%%
+%The histogram for bilingual post-editors using no alignments skewed further to the right, peaking at 8.
+%%
+%The histogram for bilingual post-editors with access to alignments skews farthest to the right, peaking at 10.

### 2015-07-10 paper/paper_table.tex
MT Summit, just before adding Isabel's latest

% !TEX root = paper.tex
% !TEX encoding = UTF-8 Unicode

\begin{table}[t]
\begin{subtable}[b]{\linewidth}
\begin{center}
\caption{Russian-English adequacy evaluation guidelines}
\label{judge_guidelines_russian}
\begin{tabular} { | c | p{120mm} | }
\hline
  12 & The post-edited translation is superior to the reference translation \\ \hline
  10 & The meaning of the Russian sentence is fully conveyed in the English translation \\ \hline
  8 & Most of the meaning of the Russian sentence is conveyed in the English translation \\ \hline
  6 & The English translation misunderstands the Russian sentence in a major way, or has many small mistakes \\ \hline
  4 & Very little information from the Russian sentence is conveyed in the English translation \\ \hline
  2 & The English translation makes no sense at all \\ \hline
\end{tabular}
\end{center}
\end{subtable}
\ \\ \ \\
\begin{subtable}[b]{\linewidth}
\begin{center}
\caption{Spanish-English adequacy evaluation guidelines}
\label{judge_guidelines_spanish}
\begin{tabular} { | c | p{120mm} | }
\hline
  10 & The meaning of the Spanish sentence is fully conveyed in the English translation \\ \hline
%  9 & The English translation contains one minor error \\ \hline
  8 & Most of the meaning of the Spanish sentence is conveyed in the English translation \\ \hline
  6 & The English translation misunderstands the Spanish sentence in a major way, or has many small mistakes \\ \hline
  4 & Very little information from the Spanish sentence is conveyed in the English translation \\ \hline
  2 & The English translation makes no sense at all \\ \hline
\end{tabular}
\end{center}
\end{subtable}
\caption{Adequacy evaluation guidelines for bilingual Russian-English human judges \citep{2014_WMT_Schwartz_etal}, and for bilingual Spanish-English human judges \citep{2009_EACL_Albrecht_etal}. Because no reference translation was available for Spanish-English, the 12 category is omitted.}
\label{judge_guidelines}
\end{table}

### 2015-07-10 paper/paper_title.tex
MT Summit, just before adding Isabel's latest

@@
 
-\title{The Effect of Word Alignments in Bilingual and Monolingual Post-Editing}
+%\title{Effects of Word Alignment Visualization on Post-Editing Quality \& Speed}
+%
+%\author{{}\\
+%	    {}\\
+%	    {}\\
+%	    {}\\
+%	    {\tt}
+%}
+%
+%\date{}
 
-\author{%
-        {}\\
-	    {}\\
-	    {}\\
-	    {}\\
-	    {\tt}
+\title{\bf Effects of Word Alignment Visualization on Post-Editing Quality \& Speed}
+
+\author{\name{\bf First Author} \hfill  \addr{author1@abc.university.country}\\ 
+        \name{\bf Second Author} \hfill \addr{author2@abc.university.country}\\ 
+        \addr{Department of Science, My University, 
+        MyTown, Zip, Country}
+\AND
+       \name{\bf Third Author} \hfill \addr{author3@abc.university.country}\\
+        \addr{Department of Science, My University, 
+        MyTown, Zip, Country}
 }
-
-\date{}

### 2015-07-10 paper/paper_methodology.tex
Merge in Isabel's methodology changes

@@
 
-We hypothesize that the presentation of word-level alignment links to human post-editors may affect the quality or speed of the resulting output, and that such effects may be dependent on the quality of the underlaying machine translations.
+We hypothesize that the presentation of word-level alignment links to human post-editors may affect the quality or speed of the resulting output, and that such effects may be dependent on the quality of the underlying machine translations.
 %
@@
 
-There were four participants who served as post-editors in the Spanish-English portion of this study, all of whom were paid for their time. 
+There were eleven participants who served as post-editors in the Spanish-English portion of this study, all of whom were paid for their time. 
 %
@@
 %
-We designate these participants as PE7--PE10.
+We designate these participants as PE7--PE17. 
 %
-The first language (L1) of all four participants was English, and all four were highly proficient in Spanish as their second language (L2). 
+The first language (L1) of all eleven participants was English, and all eleven were highly proficient in Spanish as their second language (L2). 
 %
-These participants were second year students in a university Master of Spanish Translation program.
+These participants were students in a university Master of Spanish Translation program.
 
@@
 %
-The two texts were divided up into segments that corresponded to sentences or stand alone phrases. 
+The two texts were divided up into segments that corresponded to sentences or stand-alone phrases. 
 %
@@
 %
-Post-editors 7 and 9 edited Doc C using the interface that omitted the alignments and Doc D using the interface that displayed the alignments. 
+Post-editors 7, 9, 11, 13, 15, and 17 edited Doc C using the interface that omitted the alignments and Doc D using the interface that displayed the alignments. 
 %
-Post-editors 8 and 10 edited Doc C using the interface that displayed the alignments and Doc D using the interface that omitted the alignments.
+Post-editors 8, 10, 12, 14, and 16 edited Doc C using the interface that displayed the alignments and Doc D using the interface that omitted the alignments.

### 2015-07-10 paper/paper_results.tex
Merge in Isabel's results changes

@@
 %
-The source segment was followed by the reference translation in English.
-%
-The subsequent five entries were English translations of the source segment, presented in a randomized order.
+The subsequent twelve entries were English translations of the source segment, presented in a randomized order.
 %
@@
 %
-and the four post-edited translations produced by the Spanish-English bilingual post-editors in this study.
+and the eleven post-edited translations produced by the Spanish-English bilingual post-editors in this study.
 
@@
 %
+Unlike all other participants, participant PE17 consistently produced post-edited segments of lower adequacy than the corresponding raw MT output.
+This participant was therefore dropped from all analyses of the Spanish-English data.
+
+%
 %
 %%
-%The raters were presented with blocks of six lines arranged in a vertical list: the first line was a source segment, the second was its machine translation, and below these were four translations for the segment listed in random order.
+%The raters were presented with blocks of twelve lines arranged in a vertical list: the first line was a source segment, and below these were the twelve translations for the segment listed in random order.
 %%
@@
 %
-less than one-third are judged to have major errors (ratings 2-6), while the majority (over two-thirds) are rated as mostly or completely correct (8-10).
+a minority (about two-fifths) are judged to have major errors (ratings 2-6), while the majority (about three-fifths) are rated as mostly or completely correct (8-10).
 
@@
 
-The mean adequacy score when Spanish bilingual participants were presented with alignments was 8.65.
-When alignments were omitted from the post-editing tool, the mean adequacy score was 8.57.
+The mean adequacy score when Spanish bilingual participants were presented with alignments was 8.22.
+When alignments were omitted from the post-editing tool, the mean adequacy score was 8.02.
 These means are not significantly different.
@@
 The times taken by the Spanish-English post-editors to post-edit each text were recorded by the keylogger to nearest millisecond.
-The mean times were 16.36 minutes for texts with alignment and 16.66 minutes for texts without alignment.
-This difference was not statistically significant.
+The mean times were 21 minutes  and 5 seconds for texts with alignment and 22 minutes and 5 seconds for texts without alignment.
+An independent samples t-test showed that these times are not significantly different from each other (t(18) = .295, p = .77.)
 %
+Participants were not given time limitations, so timing data must be interpreted with caution.
+Note, however, that the mean time with alignment is numerically shorter than the mean time without alignment.
+
 The shorter editing times for Spanish-English may in part be explained by the shorter length of these documents.
@@
 %
-On the other hand, in the Spanish-English condition, where overall MT quality is good, we observe relatively little variation in quality between the four post-editors.
+On the other hand, in the Spanish-English condition, where overall MT quality is good, we observe relatively little variation in quality between the ten post-editors.
 %
@@
 
+The keystroke logging data gathered for Spanish-English post-editors allowed the computation of Pause to Word Ratio (PWR).
+For each segment, PWR is the ratio of the number of pauses exceeding 300ms to the number of words in the MT segment; it is a measure of cognitive effort in post-editing (Lacruz & Shreve, 2012).
+Higher PWR corresponds to higher cognitive effort.
+% INSERT REF TO FIG 6 AND INSERT FIG 6
+Contrary to expectation, the mean PWR for Spanish-English post-editors was slightly higher for the segments with alignment (0.70) than for those without alignment (0.63).
+However, the numerical difference was not significant.
+
+It is possible that the effect of alignment on PWR was masked by the fact that the adequacy of the Spanish-English MT segments was generally high.
+Since our prediction is that alignment should both increase post-editing adequacy and reduce post-editing effort, the Gain to Effort Ratio, GER = (PE Rating – MT Rating)/PWR is a promising metric to investigate.
+We hypothesize that GER is higher for segments with alignment than for segments without alignment.
+
+GER for segments with alignment was 2.53, and GER for segments without alignment was 1.47.
+Our prediction was confirmed: a paired samples t-test showed that GER was higher for segments with alignment (t(9) = 2.49, p =.034.)
+%INSERT REF TO FIG 7 AND INSERT FIG 7
+
+This result suggests that GER may be a robust metric for measuring the effects of alignment on post-editing.
+It would be interesting to conduct further studies involving language pairs different from Spanish-English where the adequacy of machine translations may be lower.
+
 %Finally, in Figure \ref{fig:percentage_segments} we present histograms graphing the percentage of segments in each adequacy category.

### 2015-09-07 paper/figure3.tex
Camera-ready for MT Summit

@@
 \begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
-\begin{axis}[%scale only axis=true, width=60mm, height=73mm,
+\begin{axis}[scale only axis=true, width=120mm, height=60mm,
     ybar,
@@
    % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
-    xtick={1,2,3,4},
-    xticklabels={PE7,PE8,PE9,PE10},
+    xtick={1,2,3,4,5,6,7,8,9,10},
+    xticklabels={PE7,PE8,PE9,PE10,PE11,PE12,PE13,PE14,PE15,PE16},
 	xtick pos=left,
@@
 
+%	Adequacy with align	Adequacy w/o align
+%PE7	8.48	8.54
+%PE8	8.46	8.16
+%PE9	8.1	8.31
+%PE10	8.46	8
+%PE11	9.12	8.23
+%PE12	8.15	7.44
+%PE13	7.68	8.15
+%PE14	8.23	7.76
+%PE15	7.36	7.54
+%PE16	8.23	8
+%		
+%Note overall mean for MT is 7.14
+
 \addplot coordinates {};
-\addplot coordinates {(1,8.8) (2,8.461538461538462) (3,8.56) (4,8.76923076923077) };
-\addplot coordinates {(1,8.23076923076923) (2,8.72) (3,8.461538461538462) (4,8.88) };
-\addplot[red,sharp plot,update limits=false] coordinates { (-1,7.686274509803922) (12,7.686274509803922) };
+\addplot coordinates {(1,8.48) (2,8.46) (3,8.1) (4,8.46) (5,9.12) (6,8.15) (7,7.68) (8,8.23) (9,7.36) (10,8.23) };
+\addplot coordinates {(1,8.54) (2,8.16) (3,8.31) (4,8) (5,8.23) (6,7.44) (7,8.15) (8,7.76) (9,7.54) (10,8) };
+%\addplot coordinates {(1,8.8) (2,8.461538461538462) (3,8.56) (4,8.76923076923077) };
+%\addplot coordinates {(1,8.23076923076923) (2,8.72) (3,8.461538461538462) (4,8.88) };
+\addplot[red,sharp plot,update limits=false] coordinates { (-1,7.14) (12,7.14) };
 
@@
 \end{subfigure}
-\caption{Mean adequacy score per post-editor. The red horizontal line indicates the mean adequacy score (Russian-English: 6.1; Spanish-English: 7.7) of the unedited MT.}
+\caption{Mean adequacy score per post-editor. The red horizontal line indicates the mean adequacy score (Russian-English: 6.1; Spanish-English: 7.1) of the unedited MT.}
 \label{fig:mean_adequacy_score_per_posteditor}

### 2015-09-07 paper/figure7.tex
Camera-ready for MT Summit

--- 2015-02-27 paper/figure3.tex
@@
 
-\begin{figure*}[t]
-\begin{subfigure}[b]{.5\linewidth}
+\begin{figure}
+\begin{center}
 \begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
-\begin{axis}[
+\begin{axis}[scale only axis=true, width=40mm, height=10mm,
     ybar,
@@
     legend style={at={(0.5,1.05)},anchor=south},
-   ylabel={Mean Adequacy Score by Participant},
-   xlabel={Post-Editor},
+   ylabel={GER},
+   %xlabel={Post-Editor},
    % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
-    xtick={0,1,2,3,4,5,6},
-    xticklabels={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
+    xtick={0},
+    ytick={1.47,2.53},
+    xticklabels={""},
 	xtick pos=left,
@@
     %nodes near coords align={vertical},
-    bar width=5pt
+    bar width=20pt
     ]
 
-\addplot coordinates { (0,7.0) (0,6.1)};
-\addplot coordinates { (1,8.0) (2,9.8) (3,9.0) (4,8.2) (5,7.4) (6,7.7)};
-\addplot coordinates { (1,7.6) (2,9.3) (3,8.8) (4,7.6) (5,6.7) (6,7.1)};
+\addplot 
+	coordinates {};
+\addplot coordinates { (1,2.53)};
+\addplot coordinates { (1,1.47)};
 
-\addplot[red,sharp plot,update limits=false] 
-	coordinates {(-1,6.1) (8,6.1)};
+%\addplot[red,sharp plot,update limits=false] 
+%	coordinates {(-1,6.1) (8,6.1)};
 	%node[above] at (axis cs:3,6.1) {Unedited MT};
-
-%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
-\legend{Monolingual PE with Alignments, PE with Alignments,PE no Alignments}
-\end{axis}
-\end{tikzpicture}
-\caption{Russian-English}
-\label{fig:mean_adequacy_score_per_posteditor_ru}
-\end{subfigure}
-\begin{subfigure}[b]{.5\linewidth}
-\begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
-\begin{axis}[
-    ybar,
-    enlargelimits=0.15,
-    legend style={at={(0.5,1.05)},anchor=south},
-%   ylabel={Mean Adequacy Score by Participant},
-   xlabel={Post-Editor},
-   % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
-    xtick={1,2,3,4},
-    xticklabels={PE7,PE8,PE9,PE10},
-	xtick pos=left,
-	ytick pos=left,
-	ylabel shift={-0.15cm},
-	ymin=6,
-	ymax=10,
-    %xtick=data,
-    %nodes near coords,
-    %nodes near coords align={vertical},
-    bar width=5pt
-    ]
-
-\addplot coordinates {};
-\addplot coordinates {(1,8.8) (2,8.461538461538462) (3,8.56) (4,8.76923076923077) };
-\addplot coordinates {(1,8.23076923076923) (2,8.72) (3,8.461538461538462) (4,8.88) };
-\addplot[red,sharp plot,update limits=false] coordinates { (-1,7.686274509803922) (12,7.686274509803922) };
 
@@
 \end{tikzpicture}
-\caption{Spanish-English}
-\label{fig:mean_adequacy_score_per_posteditor_es}
-\end{subfigure}
-\caption{Mean adequacy score per post-editor. The red horizontal line indicates the mean adequacy score (Russian-English: 6.1; Spanish-English: 7.7) of the unedited MT.}
-\label{fig:mean_adequacy_score_per_posteditor}
-\end{figure*}
+\caption{Mean adequacy gain to effort ratio (GER) values for segments post-edited with alignment and without alignment. Effort is measured by pause to word ratio (PWR).}
+\label{fig:mean_ger}
+\end{center}
+\end{figure}

### 2015-09-07 paper/paper_abstract.tex
Camera-ready for MT Summit

@@
 %
-We select four news articles, and ask six Russian-English bilinguals and four Spanish-English bilinguals to post-edit English machine translation results, in some cases using alignments and in other cases without.
+We select four news articles, and ask six Russian-English bilinguals and eleven Spanish-English bilinguals to post-edit English machine translation results, in some cases using alignments and in other cases without.
 %

### 2015-09-07 paper/paper_intro.tex
Camera-ready for MT Summit

@@
 %
-In the second condition, we ask four Spanish-English bilingual translation students to post-edit two Spanish language news articles starting with relatively high quality English machine translation.
+In the second condition, we ask eleven Spanish-English bilingual translation students to post-edit two Spanish language news articles starting with relatively high quality English machine translation.
 %

### 2015-09-07 paper/paper_methodology.tex
Camera-ready for MT Summit

@@
 \subsubsection{Russian-English Bilingual Participants}
-There were six participants who served as post-editors in the Russian-English portion of this study, all of whom were paid for their time.
+There were six participants who served as post-editors in the Russian-English portion of this study, all of whom were paid for their time at the rate of \$25 for each hour or part of an hour.
 %
@@
 
-There were eleven participants who served as post-editors in the Spanish-English portion of this study, all of whom were paid for their time. 
+There were eleven participants who served as post-editors in the Spanish-English portion of this study, all of whom were paid for their time at the rate of \$25 for each hour or part of an hour. 
 %
@@
 %
+The experimenter was present in the room and manually recorded the times taken.
+%
 Post-Editors 2, 4, and 6 were assigned to post-edit Doc A using the variant 1 interface that displayed alignments, and Doc B using the variant 2 interface that omitted alignments.
@@
 %
+Timings were recorded by a keylogger.
+%
 Post-editors 7, 9, 11, 13, 15, and 17 edited Doc C using the interface that omitted the alignments and Doc D using the interface that displayed the alignments. 

### 2015-09-07 paper/paper_results.tex
Camera-ready for MT Summit

@@
 
+\vspace{-2mm}
 \section{Results}
@@
 
+\vspace{-2mm}
 \subsection{Rating Translation Adequacy}
@@
 The times taken by the Russian-English post-editors to post-edit each text were recorded manually to the nearest minute.
+%
+Participants post-edited each text without a break.
+%
+They took a break of approximately five minutes between texts.
+%
 The mean times were 33 minutes for texts with alignment and 40 minutes for texts without alignment.
+%
 This difference approached significance (p = .082).
@@
 The times taken by the Spanish-English post-editors to post-edit each text were recorded by the keylogger to nearest millisecond.
+%
+Participants post-edited each text without a break.
+%
+They took a break of approximately five minutes between texts.
+%
 The mean times were 21 minutes  and 5 seconds for texts with alignment and 22 minutes and 5 seconds for texts without alignment.
+%
 An independent samples t-test showed that these times are not significantly different from each other (t(18) = .295, p = .77.) 
@@
 Note, however, that the mean time with alignment is numerically shorter than the mean time without alignment.
-
+%
 The shorter editing times for Spanish-English may in part be explained by the shorter length of these documents.
@@
 
+\input{figure7}
+
 The keystroke logging data gathered for Spanish-English post-editors allowed the computation of Pause to Word Ratio (PWR).
-For each segment, PWR is the ratio of the number of pauses exceeding 300ms to the number of words in the MT segment; it is a measure of cognitive effort in post-editing (Lacruz & Shreve, 2012).
+For each segment, PWR is the ratio of the number of pauses exceeding 300ms to the number of words in the MT segment; it is a measure of cognitive effort in post-editing \citep{2014_Lacruz_Shreve}.
 Higher PWR corresponds to higher cognitive effort.
-% INSERT REF TO FIG 6 AND INSERT FIG 6
+%
+% Figure \Vref{fig:mean_pwr}
+%
 Contrary to expectation, the mean PWR for Spanish-English post-editors was slightly higher for the segments with alignment (0.70) than for those without alignment (0.63).
@@
 
+Figure \Vref{fig:mean_ger} \vpageref[above]{fig:mean_ger} shows GER for Spanish-English.
+%
 GER for segments with alignment was 2.53, and GER for segments without alignment was 1.47.
-Our prediction was confirmed: a paired samples t-test showed that GER was higher for segments with alignment (t(9) = 2.49, p =.034.)
+Our prediction was confirmed: a paired samples t-test showed that GER was higher for segments with alignment (t(9) = 2.49, p =.034.).
+%
+%
 %INSERT REF TO FIG 7 AND INSERT FIG 7
-
+%
 This result suggests that GER may be a robust metric for measuring the effects of alignment on post-editing.

### 2015-09-07 paper/paper_title.tex
Camera-ready for MT Summit

--- 2015-02-27 paper/paper_title.tex
@@
 
-\title{The Effect of Word Alignments in Bilingual and Monolingual Post-Editing}
+%\title{Effects of Word Alignment Visualization on Post-Editing Quality \& Speed}
+%
+%\author{{}\\
+%	    {}\\
+%	    {}\\
+%	    {}\\
+%	    {\tt}
+%}
+%
+%\date{}
 
-\author{%
-        {}\\
-	    {}\\
-	    {}\\
-	    {}\\
-	    {\tt}
+\title{\bf Effects of Word Alignment Visualization on Post-Editing Quality \& Speed}
+
+\author{\name{\bf Lane Schwartz} \hfill  \addr{lanes@illinois.edu}\\ 
+        \addr{Dept. of Linguistics, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA}
+\AND
+        \name{\bf Isabel Lacruz} \hfill \addr{ilacruz@kent.edu}\\ 
+       \name{\bf Tatyana Bystrova} \hfill \addr{tbystro2@kent.edu}\\
+        \addr{Dept. of Modern \& Classical Language Studies, Kent State University, Kent, OH 44242, USA}
 }
-
-\date{}

### 2015-09-07 data.acl/ru-en/data/scored/calculate_per_category_percentages.sh

@@ -1,0 +1,23 @@
+#!/bin/bash
+
+codes="en s0-en s1-en s2-en s3-en s4-en s5-en s6-en"
+docs="doc110 doc130"
+
+for code in ${codes}; do
+
+	if [[ "${code}" == "en" ]]; then
+		user="moses"	
+	else
+		user="${code}"
+	fi
+	
+	for doc in ${docs}; do
+		./calculate_per_category_percentages.rb < ${doc}.${user}.scores > ${doc}.${user}.percentages
+	done
+
+done
+
+
+for doc in ${docs}; do
+	paste ${doc}.moses.percentages ${doc}.s*-en.percentages > ${doc}.percentages.csv
+done

### 2015-09-07 mt_summit_supplement/code/src/Controller.scala

@@ -1,0 +1,141 @@
+
+import TranslatedDocuments
+import TranslatedDocument
+import java.util.Scanner
+import scala.collection.mutable.ArrayBuffer
+import java.io.File
+import edu.illinois.linguistics.postedit.ParallelSentence
+
+
+class AFRL_WMT_2014_ParallelDocuments(documents : IndexedSeq[TranslatedDocument], val postEditedPath : String) extends TranslatedDocuments(documents) {
+
+  override def save() : Boolean = {
+    
+    import java.io.BufferedWriter
+    import java.io.OutputStreamWriter
+
+    import java.io.FileOutputStream
+    import java.io.IOException
+    
+    var success = true;
+
+    var out : BufferedWriter = null;
+    try {
+      out = new BufferedWriter(new OutputStreamWriter(new FileOutputStream(postEditedPath), "UTF-8"));
+      out.write("=================================");
+      out.newLine();
+      out.write("=================================");
+      out.newLine();
+      documents.foreach { document => 
+        document.foreach { parallelSentence => 
+          out.write(parallelSentence.editedTranslation);
+          out.newLine();
+        }
+        out.write("=================================");
+        out.newLine();
+        out.write("=================================");
+        out.newLine();
+      }
+    } catch {
+      case e: IOException => {
+        success = false;
+        e.printStackTrace();
+      }
+    } finally {
+      if (out!=null) {
+        try {
+          out.close();
+        } catch {
+          case e: IOException => {
+            success = false;
+            e.printStackTrace();
+          }
+        }
+      }
+    }
+    
+    return success;
+  }
+    
+}
+
+object AFRL_WMT_2014_ParallelDocumentsReader {
+  
+  def collateTranslatedDocuments(postEditedPath:String, sourcePath:String, targetPath:String, alignmentsPath:String) : TranslatedDocuments = {
+    
+    val list = new ArrayBuffer[TranslatedDocument] 
+    val parallelSentences = new ArrayBuffer[ParallelSentence]
+
+    val postEditScanner = new Scanner(new File(postEditedPath), "UTF-8")
+    val sourceScanner = new Scanner(new File(sourcePath), "UTF-8")
+    val targetScanner = new Scanner(new File(targetPath), "UTF-8")
+    val alignmentsScanner = new Scanner(new File(alignmentsPath), "UTF-8")
+
+    try {
+      
[…]

### 2015-09-07 mt_summit_supplement/code/src/EventLogger.scala

@@ -1,0 +1,297 @@
+
+import java.awt.Component
+import java.awt.Container
+import java.awt.event.ComponentEvent
+import java.awt.event.FocusEvent
+import java.awt.event.FocusListener
+import java.awt.event.KeyEvent
+import java.awt.event.KeyListener
+import java.awt.event.MouseEvent
+import java.awt.event.MouseListener
+import java.awt.event.MouseMotionListener
+import java.awt.event.MouseWheelEvent
+import java.awt.event.MouseWheelListener
+import java.io.FileOutputStream
+import java.io.IOException
+import java.io.OutputStreamWriter
+import java.io.UnsupportedEncodingException
+import java.io.Writer
+import java.util.zip.GZIPOutputStream
+import java.util.zip.ZipOutputStream
+
+
+class EventLogFormatter() {
+  
+  private var startTime = -1L;
+  
+  protected def elapsedMilliseconds() : Long = {
+    
+    if (startTime < 0) {
+      startTime = System.currentTimeMillis();
+    }
+
+    val now = System.currentTimeMillis();
+    val elapsed = now - startTime;
+    return elapsed
+    
+  }
+  
+  def shouldLog(e:ComponentEvent) : Boolean = {
+    e.getComponent() match {
+      case _:EditField                => return true
+      case _:ParallelSentencePanel    => return true
+      case _:SourceWordLabel          => return true
+      case _:TargetWordLabel          => return true
+      case _                          => return false
+    }
+  }
+  
+  def eventType(e:ComponentEvent) : String = {
+    e.getID match {
+      case MouseEvent.MOUSE_PRESSED  => return "MOUSE_PRESSED"
+      case MouseEvent.MOUSE_RELEASED => return "MOUSE_RELEASED" 
+      case MouseEvent.MOUSE_CLICKED  => return "MOUSE_CLICKED"
+      case MouseEvent.MOUSE_ENTERED  => return "MOUSE_ENTERED"
+      case MouseEvent.MOUSE_EXITED   => return "MOUSE_EXITED"
+      case MouseEvent.MOUSE_MOVED    => return "MOUSE_MOVED"
+      case MouseEvent.MOUSE_DRAGGED  => return "MOUSE_DRAGGED"
+      case MouseEvent.MOUSE_WHEEL    => return "MOUSE_WHEEL"
+      case KeyEvent.KEY_PRESSED      => return "KEY_PRESSED"
[…]

### 2015-09-07 mt_summit_supplement/code/src/Model.scala

@@ -1,0 +1,214 @@
+
+import scala.collection.mutable.ArrayBuffer
+import scala.collection.mutable.SortedSet
+import scala.collection.mutable.TreeSet
+
+abstract class TranslatedDocuments(val documents : IndexedSeq[TranslatedDocument]) extends IndexedSeq[TranslatedDocument] {
+
+  def length() : Int = {
+    return documents.length
+  }
+  
+  def apply(index:Int) : TranslatedDocument = {
+    return documents(index)
+  }
+
+  override def iterator() : Iterator[TranslatedDocument] = {
+    return documents.iterator
+  }
+
+  def save() : Boolean
+  
+}
+
+class TabDelineatedTranslatedDocuments(documents : IndexedSeq[TranslatedDocument], val postEditedPath : String) extends TranslatedDocuments(documents) {
+  override def save() : Boolean = {
+    
+    import java.io.BufferedWriter
+    import java.io.OutputStreamWriter
+
+    import java.io.FileOutputStream
+    import java.io.IOException
+    
+    var success = true;
+
+    var out : BufferedWriter = null;
+    try {
+      out = new BufferedWriter(new OutputStreamWriter(new FileOutputStream(postEditedPath), "UTF-8"));
+//      out.write("=================================");
+//      out.newLine();
+//      out.write("=================================");
+//      out.newLine();
+      documents.foreach { document => 
+        document.foreach { parallelSentence => 
+          out.write(parallelSentence.editedTranslation);
+          out.newLine();
+        }
+//        out.write("=================================");
+        out.newLine();
+//        out.write("=================================");
+//        out.newLine();
+      }
+    } catch {
+      case e: IOException => {
+        success = false;
+        e.printStackTrace();
+      }
+    } finally {
+      if (out!=null) {
+        try {
+          out.close();
+        } catch {
+          case e: IOException => {
+            success = false;
+            e.printStackTrace();
+          }
+        }
+      }
+    }
+    
+    return success;
+  }  
+}
+
+object TabDelineatedTranslatedDocuments {
+  
+  
+  def get(dataPath:String, resultsPath:String, showAlignments:Boolean, showSource:Boolean, showMT:Boolean) : TabDelineatedTranslatedDocuments = {
+    
+    import java.util.Scanner
+    import java.io.File
+    
[…]

### 2015-09-07 mt_summit_supplement/code/src/PostEditor.java

@@ -1,0 +1,285 @@
+import java.awt.GridLayout;
+import java.awt.Insets;
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+import java.io.File;
+import java.util.Calendar;
+import java.util.prefs.Preferences;
+
+import javax.swing.BoxLayout;
+import javax.swing.JButton;
+import javax.swing.JCheckBox;
+import javax.swing.JFileChooser;
+import javax.swing.JFrame;
+import javax.swing.JLabel;
+import javax.swing.JPanel;
+import javax.swing.JTextArea;
+import javax.swing.JTextField;
+import javax.swing.SwingUtilities;
+import javax.swing.UIManager;
+import javax.swing.event.DocumentEvent;
+import javax.swing.event.DocumentListener;
+
+import EventLogger;
+import PostEditorControllerWithMenu;
+import TabDelineatedTranslatedDocuments;
+import TranslatedDocuments;
+
+
+public class PostEditor implements Runnable {
+	
+	@SuppressWarnings("serial")
+	private class FileChooser extends JPanel implements ActionListener, DocumentListener {
+	    private final JButton dataButton, continueButton;
+	    private final JLabel resultsLabel, logLabel, subjectLabel;
+	    public final JCheckBox alignmentsButton, sourceButton, mtButton, timestampButton;
+	    public final JTextArea dataArea, resultsArea, logArea;
+	    private final JTextField subjectArea;
+	    private final JFileChooser fc;
+	    private final String timestamp;
+//	    private String resultsPath, logPath;
+	    
+	    private final Preferences prefs;
+	    
+	    FileChooser() {
+	        super(new GridLayout(0,2));
+	        
+            Calendar now = Calendar.getInstance();
+            int year   = now.get(Calendar.YEAR);
+            int month  = now.get(Calendar.MONTH);
+            int day    = now.get(Calendar.DAY_OF_MONTH);
+            int hour   = now.get(Calendar.HOUR_OF_DAY);
+            int minute = now.get(Calendar.MINUTE);
+            int second = now.get(Calendar.SECOND);
+            this.timestamp = String.format("%04d-%02d-%02d_%02d-%02d-%02d", year, month, day, hour, minute, second);
+
+	        
+	        prefs = Preferences.userNodeForPackage(PostEditor.class);
+
+	        dataArea = new JTextArea(1,50);
+	        dataArea.setMargin(new Insets(5,5,5,5));
+	        dataArea.setEditable(false);
+	        
[…]

### 2015-09-07 mt_summit_supplement/code/src/Split.scala

@@ -1,0 +1,160 @@
+
+import scala.collection.Map
+import scala.collection.mutable.ArrayBuffer
+import scala.collection.mutable.SortedSet
+import scala.collection.mutable.TreeSet
+
+class Split(source:String, target:String, charPointsString:String) {
+
+//  println("Hello")
+  
+//  val source="Sie fragen: Will die Regierung in Berlin uns erniedrigen?"
+//  val target="You ask: us wants to humiliate the Government in Berlin?"
+//  val charPointsString="0:2-0:2 4:9-4:6 10:10-7:7 12:15-12:19 17:19-31:33 21:29-35:44 31:32-46:47 34:39-49:54 41:43-9:10 45:55-21:29 56:56-55:55"
+
+//  def split(source:String, target:String, charPointsString:String) : (Seq[String], Map[String,Int], Seq[String], Map[String,Int]) = {
+//  println(source)
+//  println(target)
+//  println()
+	private val charPoints=charPointsString.split("\\s+")
+  private val sourceCharPoints = charPoints.map( p => p.split("-")(0) )
+  private val targetCharPoints = charPoints.map( p => p.split("-")(1) )
+  
+  private val sourceCharStartPoints = sourceCharPoints.map ( p => p.split(":")(0).toInt )
+  private val sourceCharEndPoints   = sourceCharPoints.map ( p => p.split(":")(1).toInt )
+  
+  private val targetCharStartPoints = targetCharPoints.map ( p => p.split(":")(0).toInt )
+  private val targetCharEndPoints   = targetCharPoints.map ( p => p.split(":")(1).toInt )
+  
+  private val sourceBoundaryPoints:SortedSet[Int] = new TreeSet[Int]
+  private val targetBoundaryPoints:SortedSet[Int] = new TreeSet[Int]
+  
+	sourceBoundaryPoints.add(0)
+  targetBoundaryPoints.add(0)
+  
+  sourceBoundaryPoints.add(source.length)
+  targetBoundaryPoints.add(target.length)
+
+//  private def spaceIndices(string:String) : SortedSet[Int] = {
+//    
+//	  val set = new TreeSet[Int]
+//    
+//		var index = string.indexOf(" ")
+//    
+//		while (index > 0) {
+//			set.add(index)
+//			index = string.indexOf(" ", index+1)
+//		}
+//    
+//	  return set
+//    
+//  }
+//
[…]

### 2015-09-07 mt_summit_supplement/code/src/View.scala

@@ -1,0 +1,247 @@
+
+import java.awt.Color
+import java.awt.Container
+import java.awt.Dimension
+import java.awt.FlowLayout
+import java.awt.Frame
+import java.awt.Graphics2D
+import java.awt.Graphics
+import java.awt.RenderingHints
+import java.awt.Rectangle
+import java.awt.Point
+import java.awt.Toolkit
+import java.awt.event.KeyEvent
+import javax.swing.Box
+import javax.swing.BoxLayout
+import javax.swing.JFrame
+import javax.swing.JLabel
+import javax.swing.JMenu
+import javax.swing.JMenuBar
+import javax.swing.JMenuItem
+import javax.swing.JPanel
+import javax.swing.JScrollPane
+import javax.swing.JTextField
+import javax.swing.KeyStroke
+import javax.swing.Scrollable
+import javax.swing.ScrollPaneConstants
+import javax.swing.ScrollPaneLayout
+import java.awt.Font
+
+
+class EditField(val parallelSentence:ParallelSentence) extends JTextField(parallelSentence.editedTranslation, 0) {
+  
+  this.setFont(new Font(this.getFont().getName(), Font.PLAIN, 18))
+  
+  EditFieldController.register(this)
+  
+}
+
+class SourceWordLabel(val parallelSentence:ParallelSentence, val sourceIndex:Int) extends JLabel {
+  
+  this.setFont(new Font(this.getFont().getName(), Font.PLAIN, 18))
+  
+  override def getText() : String = {
+    return parallelSentence.sourceWords(sourceIndex)
+  }
+}
+
+class TargetWordLabel(val parallelSentence:ParallelSentence, val targetIndex:Int) extends JLabel {
+  
+  this.setFont(new Font(this.getFont().getName(), Font.PLAIN, 18))
+//  this.setBorder(javax.swing.BorderFactory.createLineBorder(Color.black))
+  
+  override def getText() : String = {
+    return parallelSentence.targetWords(targetIndex)
+  }
+}
+
+class SourceSentencePanel(val parallelSentence:ParallelSentence) extends JPanel(new FlowLayout(FlowLayout.LEFT, 0, 5)) {
+  
+  val words : Seq[SourceWordLabel] = parallelSentence.sourceWordIndices.map({ sourceWordIndex:Int => new SourceWordLabel(parallelSentence,sourceWordIndex)})
+  
+  words.foreach { word => 
+    this.add(word)
[…]

### 2015-09-07 mt_summit_supplement/data/es-en/analysis.pt3/calculate-total-times.sh

@@ -1,0 +1,19 @@
+#!/bin/bash
+
+subjects=$(cd results; ls -1)
+
+echo -e "Subject\tDocument\tTime (milliseconds)\tAlignments shown"
+
+for subject in ${subjects}; do
+
+	for doc in 1 2; do
+	
+		time=$(tail -n 1 results/${subject}/mt.es-en.${doc}.*.log.txt | cut -f 1)
+		alignments=$(grep "Showing alignments" results/${subject}/mt.es-en.${doc}.*.log.txt | sed 's,.*:\s,,')
+		
+		
+		echo -e "${subject}\t${doc}\t${time}\t${alignments}"
+	
+	done
+
+done

### 2015-09-07 mt_summit_supplement/data/ru-en/data/scored/calculate-means.rb

@@ -1,0 +1,46 @@
+#!/usr/bin/ruby
+
+data=Array.new
+keys=nil
+
+STDIN.each_line {|line|
+
+	if line=~/[[:alpha:]]/
+		keys=line.split
+	else
+		data.push(line.split)
+	end
+
+}
+
+sums=Array.new(keys.size) { 0.0 }
+means=Array.new(keys.size) { 0.0 }
+
+sums_of_differences=Array.new(keys.size) { 0.0 }
+means_of_differences=Array.new(keys.size) { 0.0 }
+
+data.each{ |row|
+
+	row.each_with_index{|value,index|
+		sums[index] += value.to_i
+		sums_of_differences[index] += (value.to_i - row[0].to_i)
+	}
+
+}
+
+
+sums.each_with_index{ |sum,index|
+	means[index] = sum/data.size
+}
+
+sums_of_differences.each_with_index{ |sum,index|
+	means_of_differences[index] = sum/data.size
+}
+
+
+puts keys.join(" & ")
+puts means.join(" & ")
+puts
+puts
+puts keys.join(" & ")
+puts means_of_differences.join(" & ")

### 2015-09-07 mt_summit_supplement/data/ru-en/data/scored/extract-individual-results.sh

@@ -1,0 +1,27 @@
+#!/bin/bash
+
+codes="en s0-en s1-en s2-en s3-en s4-en s5-en s6-en"
+docs="doc110 doc130"
+
+for code in ${codes}; do
+
+	if [[ "${code}" == "en" ]]; then
+		user="moses"	
+	else
+		user="${code}"
+	fi
+	
+	
+	grep "\t${code}$" final-results.csv > "final-results.${user}.csv"
+
+	for doc in ${docs}; do
+		echo "${user}" > ${doc}.${user}.scores
+		grep "\t${code}$" final-results.csv | grep "^${doc}" | cut -f 3 >> ${doc}.${user}.scores
+	done
+
+done
+
+
+for doc in ${docs}; do
+	paste ${doc}.moses.scores ${doc}.s*-en.scores > ${doc}.scores.csv
+done

### 2015-09-07 mt_summit_supplement/data/ru-en/data/scored/which_edits_are_better_than_MT.rb

@@ -1,0 +1,29 @@
+#!/usr/bin/ruby
+
+line_number=0
+STDIN.each_line{ |line|
+
+	if line=~/[[:alpha:]]/
+		puts line.strip.split.join(" & ")+' \\\\ \hline'
+	else
+		parts=line.strip.split
+		final_parts=Array.new(parts.size)
+		
+		parts.each_with_index { |part,index|
+		
+			if part.to_i > parts[0].to_i
+				final_parts[index] = "\\textbf{#{part}}"
+			elsif part.to_i < parts[0].to_i
+				final_parts[index] = "\\textcolor{red}{\\textit{#{part}}}"
+			else
+				final_parts[index] = part
+			end
+		
+		}
+		
+		puts "B#{line_number} & " + final_parts.join(" & ")+' \\\\ \hline'
+		line_number += 1
+	end
+
+	
+}

### 2015-09-07 mt_summit_supplement/scripts/create_graphs.rb

@@ -1,0 +1,265 @@
+#!/usr/bin/ruby
+
+
+class DataPoint
+
+	attr_reader :doc, :sentence_number, :who, :score, :alignment
+
+	def initialize(line)
+	
+		parts = line.gsub('\n','').split("\t")
+	
+		@doc=parts[0].strip
+		@sentence_number=parts[1].strip.to_i
+		@who=parts[2].strip
+		@score=parts[3].strip.to_i
+		@alignment=parts[4].strip
+		if @alignment=="true"
+			@alignment=true
+		elsif @alignment=="false"
+			@alignment=false
+		end
+	
+	end
+
+	def is_mt()
+		return @who=="mt"
+	end
+
+	def sentence_id()
+		return "#{@doc}_#{@sentence_number}"
+	end
+
+	def to_s()
+		return "#{@doc}\t#{@sentence_number}\t#{@who}\t#{@score}\t#{@alignment}"
+	end
+
+	def <=> other
+    	return self.sentence_id() <=> other.sentence_id()
+ 	end
+ 	
+ 	def to_f
+ 		return self.score
+ 	end
+
+end
+
+class SentenceData
+
+	attr_reader :mt, :data
+
+	def initialize()
+		@data=Array.new
+		@mt=nil
+	end
+
+	def add(dataPoint)
+		if (dataPoint.is_mt())
+			@mt=dataPoint
+		else
+			@data.push(dataPoint)
+		end
+	end
+
+	def mt_score()
+		return @mt.score
+	end
+
+ 	def <=> other
+    	self.mt <=> other.mt
+  	end
+
+	def to_s()
+		return "#{self.mt.to_s} with #{self.data.size} points"
+	end
+
+end
+
+def mean(array)
+	
+	sum=0.0
+	
+	array.each{|dataPoint|
+		#sum += dataPoint.score
+		sum += dataPoint.to_f
+	}
+	
+	return sum/array.size
+	
+end
+
+data_per_sentence=Hash.new{|k,v| k[v]=SentenceData.new}
+
+File.open("analysis/scored_breakdown.updated.tsv", "r") { |file|
+  file.each_line{ |line|
+
+	d=DataPoint.new(line)
+	
+	data_per_sentence[d.sentence_id()].add(d)
+
+  }
+}
+
+just_mt=Array.new
+data_per_mt_score=Hash.new{|k,v| k[v]=Array.new}
+
[…]

### 2015-09-07 mt_summit_supplement/scripts/focus.rb

@@ -1,0 +1,68 @@
+#!/usr/bin/ruby
+
+times=Hash.new{|k,v| k[v]=Array.new}
+
+last_seen_time=0
+last_seen_sentence_number=0
+
+STDIN.each_line {|line|
+	
+	unless (line.start_with?("#"))
+
+		parts=line.split("\t")
+		#puts parts[4]
+		
+		timestamp=parts[0].strip.to_i
+		last_seen_time=timestamp
+		event_type=parts[1].strip
+		sentence_number=parts[4].strip.to_i
+	
+		if (event_type=="FOCUS_GAINED")
+			times[sentence_number].push(timestamp)
+			last_seen_sentence_number=sentence_number
+		elsif (event_type=="FOCUS_LOST")
+			start=times[sentence_number].pop
+			times[sentence_number].push(timestamp-start)
+		end	
+	
+	end
+}
+
+			start=times[last_seen_sentence_number].pop
+			times[last_seen_sentence_number].push(last_seen_time-start)
+
+
+def alignments_were_present(doc,who)
+
+	if (who=="mt")
+		return ""
+	end
+
+	if (doc=="es-en.1")
+		if (who=="s1" || who=="s3")
+			return false
+		elsif (who=="s2" || who=="s4")
+			return true
+		else
+			raise "ERROR:\t#{doc}\t\#{who}"
+		end
+	elsif (doc=="es-en.2")
+		if (who=="s1" || who=="s3")
+			return true
+		elsif (who=="s2" || who=="s4")
+			return false
+		else
+			raise "ERROR:\t#{doc}\t\#{who}"
+		end	
+	else
+		raise "ERROR:\t#{doc}\t\#{who}"
+	end
+
+end
+
+times.keys.sort.each{|sentence_number|
+	sum=times[sentence_number].inject(0, :+)
+	a=alignments_were_present(ARGV[0],ARGV[1])
+	puts "#{ARGV[0]}\t#{sentence_number}\t#{sum}\t#{a}"
+	#	puts "#{sentence_number}\t#{sum} milliseconds\t#{sum/1000} seconds\t#{sum/1000/60} minutes"
+}

### 2015-09-07 mt_summit_supplement/code/src/Controller.scala
Added license text

@@ -1,3 +1,4 @@
+// This Source Code Form is subject to the terms of the Mozilla Public License, v. 2.0. If a copy of the MPL was not distributed with this file, You can obtain one at http://mozilla.org/MPL/2.0/.
 
 import TranslatedDocuments
 import TranslatedDocument

### 2015-09-07 mt_summit_supplement/code/src/EventLogger.scala

@@ -1,3 +1,4 @@
+// This Source Code Form is subject to the terms of the Mozilla Public License, v. 2.0. If a copy of the MPL was not distributed with this file, You can obtain one at http://mozilla.org/MPL/2.0/.
 
 import java.awt.Component
 import java.awt.Container

### 2015-09-07 mt_summit_supplement/code/src/Model.scala

@@ -1,3 +1,4 @@
+// This Source Code Form is subject to the terms of the Mozilla Public License, v. 2.0. If a copy of the MPL was not distributed with this file, You can obtain one at http://mozilla.org/MPL/2.0/.
 
 import scala.collection.mutable.ArrayBuffer
 import scala.collection.mutable.SortedSet

### 2015-09-07 mt_summit_supplement/code/src/Split.scala

@@ -1,3 +1,4 @@
+// This Source Code Form is subject to the terms of the Mozilla Public License, v. 2.0. If a copy of the MPL was not distributed with this file, You can obtain one at http://mozilla.org/MPL/2.0/.
 
 import scala.collection.Map
 import scala.collection.mutable.ArrayBuffer

### 2015-09-07 mt_summit_supplement/code/src/View.scala

@@ -1,3 +1,4 @@
+// This Source Code Form is subject to the terms of the Mozilla Public License, v. 2.0. If a copy of the MPL was not distributed with this file, You can obtain one at http://mozilla.org/MPL/2.0/.
 
 import java.awt.Color
 import java.awt.Container

### 2015-09-07 paper/paper_methodology.tex
Added link to github repo in paper

@@
 % !TEX encoding = UTF-8 Unicode
-
+\vspace{-1.5mm}
 \section{Methodology}
 \label{sec:methodology}
-
+\vspace{-1.5mm}
 We hypothesize that the presentation of word-level alignment links to human post-editors may affect the quality or speed of the resulting output, and that such effects may be dependent on the quality of the underlying machine translations.

### 2015-09-07 paper/paper_results.tex
Added link to github repo in paper

@@
 
-Following the methodology outlined in \S\ref{sec:translation_quality}, all post-edited output as well as all machine translations were evaluated by bilingual human judges using the adequacy scales shown in Table~\ref{judge_guidelines} \vpageref{judge_guidelines}.
+Following the methodology outlined in \S\ref{sec:translation_quality}, all post-edited output as well as all machine translations were evaluated by bilingual human judges using the adequacy scales shown in Table~\ref{judge_guidelines}.
+% \vpageref{judge_guidelines}.
 
